### 2025-02-28 Manuscript_Drafts.Rmd
manuscript stuff

---
title: "manuscript_stuff"
author: "Kristen Johnson"
date: "2025-02-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

OPTION 1:

Introduction: The Feathered Balance Sheet: A Mixed Methods Examination of Urban Backyard Chicken Husbandry
In recent decades, the practice of maintaining domestic poultry within urban and suburban residential settings has experienced a notable resurgence. This phenomenon, colloquially referred to as "backyard chicken keeping," represents a fascinating intersection of agricultural tradition and contemporary sustainability movements. The economic landscape has further accelerated this trend, as inflated egg prices have prompted an increasing number of households to consider domestic poultry as a pragmatic response to marketplace volatility. Indeed, consumer data suggests that the correlation between rising commercial egg costs and the purchase of chicken coops is remarkably robust.
The quantitative and qualitative dimensions of this investigation address a critical gap in the literature, which has hitherto focused either on large-scale commercial poultry operations or on historical agricultural practices. While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution—a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate.
Current Study
Our research design employs a mixed methods approach to develop a nuanced understanding of this increasingly common practice. The methodology combines quantitative data analysis examining multiple factors related to backyard chicken husbandry—including cost-benefit analyses, time investment, and zoning compliance—with qualitative thematic analysis of in-depth interviews conducted with chicken owners across three metropolitan areas. By triangulating these methodological approaches, we aspire to move beyond anecdotal evidence and develop an empirically robust understanding of what might be termed the "net hennefit" of backyard chicken husbandry in contemporary urban contexts. The present study thus investigates the hypothesis that the benefits of maintaining a small flock of Gallus gallus domesticus in residential settings significantly outweigh the associated challenges and drawbacks.

OPTION 2:

Introduction
Backyard chicken keeping has surged in popularity in recent years, driven by a desire for sustainable food production, self-sufficiency, and ethical animal husbandry (_______CITE_________). While much of the existing literature focuses on small and medium-sized breeds, large chicken breeds—such as Brahmas, Jersey Giants, and Orpingtons—offer unique advantages and challenges for backyard poultry enthusiasts. These birds often provide higher egg production, greater meat yield, and a more docile temperament, making them attractive to small-scale farmers and homesteaders (_______CITE_________). However, their size also necessitates specialized care, including adjustments in nutrition, housing, and health management.  
Despite the growing interest in raising large chickens in non-commercial settings, research remains limited on how backyard keepers manage the specific needs of these birds. Understanding the factors that contribute to their well-being—such as space requirements, dietary considerations, and health monitoring—is crucial for promoting sustainable and humane poultry practices. Furthermore, the motivations, experiences, and challenges of backyard chicken keepers remain underexplored, particularly regarding the balance between productivity and ethical care (_______CITE_________).  
This study employs a mixed methods approach to examine the care and management of large chicken breeds in backyard settings. Using surveys and interviews with backyard poultry keepers, alongside observational data on bird health and environmental conditions, we aim to identify best practices and common challenges in raising these birds. By integrating qualitative and quantitative data, this research seeks to provide a comprehensive understanding of how backyard poultry keepers navigate the complexities of raising large chickens. The findings will contribute to the broader discourse on sustainable animal husbandry and inform best practices for individuals seeking to maintain healthy, productive backyard flocks.

### 2025-02-28 Manuscript_Final.qmd
manuscript stuff

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:
  - name: W. Joel Schneider
    corresponding: true
    orcid: 0000-0002-8393-5316
    email: schneider@temple.edu
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 1301 Cecil B. Moore Ave.
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
    role:
      - writing
      - conceptualization
  - name: Fulano Zutano Mengano
    affiliations: Universidad de Dondequiera
    orcid: 0000-0000-0000-0001
    role:
      - formal anlaysis
      - visualization
      - editin
  - name: Thomas Richard Harris
    affiliations: 
      - name: Generic State University
        department: Department of Scholarly Studies
    orcid: 0000-0000-0000-0002
    role:
      - editing
      - funding acquistion
  - name: Wut C. Whosis
    affiliations: Whatchama College
    orcid: 0000-0000-0000-0003
    role:
      - software
      - methodology
      - editing
- name: Natalie Dowling
corresponding: true
orcid: 0000-0002-7190-1979
email: ndowling@uchicago.edu
affiliations:
- name: University of Chicago
department: Master of Arts Program in the Social Sciences
address: 5801 S. Ellis Ave.
city: Chicago
region: IL
postal-code: 60637
abstract: "This and fi l e shows the basic format for a Quarto notebook using the
'apaquarto' extension, which provides a template for APA style manuscripts. The
YAML header includes some properties that will be commonly used, but there are
many more options. The body of the notebook includes markdown text and code
chunks, and references can be included using a BibTeX file. When the document is
rendered, the output will be rendered in APA style."
keywords: [quarto, tutorials, R language]
a u t h o r - n o t e :
d i s c l o s u r e s :
conflict of interest: The author has no conflict of interest to declare.
references. bib # create a b i b file in the root directory of your
project
f o r m a t :
#apaquarto-docx: default # you can render your project in html, doc, and/or pdf
apaquarto-html: default
comment out some as you're working and don't need them
format: pdf
---

```{r}
setwd("/Users/kristenjohnson/KristenWorkingDirectory/That-s-a-BigAss-Chicken/temp")
quarto::quarto_use_template("wjschne/apaquarto", no_prompt
= TRUE)
```

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2025-02-28 Manuscript_Drafts.Rmd
Author information and sections for paper

@@
 ---
+author:
+  - name: Karen Veronica Becerra
+    orcid:0009-0006-4967-0955
+    email: kvbecerra@Uchicago.edu 
+    affiliations:
+      - name: The University of Chicago 
+        department: Division of the Social Sciences Psychology 
+        address: 5801 S Ellis Ave
+        city: Chicago
+        region: IL
+        country: USA
+        postal-code: 60637
 
@@
 The findings will contribute to the broader discourse on sustainable animal husbandry and inform best practices for individuals seeking to maintain healthy, productive backyard flocks.
+Abstract
+Introduction 
+Current study 
+Methods
+Results 
+Discussion 
+References

### 2025-02-28 Manuscript_Final.qmd
bibliography stuff

@@
 author:
-  - name: W. Joel Schneider
-    corresponding: true
-    orcid: 0000-0002-8393-5316
-    email: schneider@temple.edu
-    affiliations:
-      - name: Temple University
-        department: College of Education and Human Development
-        address: 1301 Cecil B. Moore Ave.
-        city: Philadelphia
-        region: PA
-        postal-code: 19122-6091
-    role:
-      - writing
-      - conceptualization
-  - name: Fulano Zutano Mengano
-    affiliations: Universidad de Dondequiera
-    orcid: 0000-0000-0000-0001
-    role:
-      - formal anlaysis
-      - visualization
-      - editin
-  - name: Thomas Richard Harris
-    affiliations: 
-      - name: Generic State University
-        department: Department of Scholarly Studies
-    orcid: 0000-0000-0000-0002
-    role:
-      - editing
-      - funding acquistion
-  - name: Wut C. Whosis
-    affiliations: Whatchama College
-    orcid: 0000-0000-0000-0003
-    role:
-      - software
-      - methodology
-      - editing
+
 - name: Natalie Dowling
@@
 keywords: [quarto, tutorials, R language]
-a u t h o r - n o t e :
-d i s c l o s u r e s :
+author-note:
+  disclosures:
     conflict of interest: The author has no conflict of interest to declare.
-references. bib # create a b i b file in the root directory of your
-project
-f o r m a t :
-#apaquarto-docx: default # you can render your project in html, doc, and/or pdf
-apaquarto-html: default
-comment out some as you're working and don't need them
-format: pdf
+bibliography: # create a bib file in the root directory of your project
+format:
+  #apaquarto-docx: default 
+  apaquarto-html: default    # remember to reverse commenting out other formats
+  apaquarto-pdf: default
 ---
@@
 ```{r}
-setwd("/Users/kristenjohnson/KristenWorkingDirectory/That-s-a-BigAss-Chicken/temp")
-quarto::quarto_use_template("wjschne/apaquarto", no_prompt
-= TRUE)
+
 ```
 
-## Quarto
+Chickens are pretty great [@elkhoraibiBackyardChickensUnited2014; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard].
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
-
-## Running Code
-
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r}
-1 + 1
-```
-
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
-```
-
-The `echo: false` option disables the printing of code (only output is displayed).
+/clear
+# References

### 2025-03-01 Manuscript_Final.qmd
more data on chickens as well as a qmd update

@@
 author:
-
-- name: Natalie Dowling
-corresponding: true
-orcid: 0000-0002-7190-1979
-email: ndowling@uchicago.edu
+  - name: Karen Veronica Becerra
+    orcid: 0009-0006-4967-0955
+    email: kvbecerra@Uchicago.edu 
     affiliations:
-- name: University of Chicago
-department: Master of Arts Program in the Social Sciences
-address: 5801 S. Ellis Ave.
+      - name: The University of Chicago 
+        department: Division of the Social Sciences Psychology 
+        address: 5801 S Ellis Ave
         city: Chicago
         region: IL
+        country: USA
         postal-code: 60637
-abstract: "This and fi l e shows the basic format for a Quarto notebook using the
-'apaquarto' extension, which provides a template for APA style manuscripts. The
-YAML header includes some properties that will be commonly used, but there are
-many more options. The body of the notebook includes markdown text and code
-chunks, and references can be included using a BibTeX file. When the document is
-rendered, the output will be rendered in APA style."
-keywords: [quarto, tutorials, R language]
+  - name: Kristen M. Johnson
+    orcid: 
+    email: kvbecerra@Uchicago.edu 
+    affiliations:
+      - name: The University of Chicago 
+        department: Division of the Social Sciences Psychology 
+        address: 5801 S Ellis Ave
+        city: Chicago
+        region: IL
+        country: USA
+        postal-code: 60637
+
+abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices.
+Employing a mixed methods approach, we analyzed quantitative data from 157 participants across three metropolitan areas to assess economic factors, time investment, and regulatory compliance associated with domestic poultry husbandry.
+Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges.
+Our findings indicate that while initial setup costs average $487, households recover this investment within 14 months through egg production, with additional benefits including reduced food waste, improved garden soil quality, and reported increases in household well-being.
+Challenges identified include time commitment (averaging 28 minutes daily), navigating municipal regulations, and managing seasonal variations in productivity.
+Factor analysis revealed that success factors cluster around three dimensions: appropriate infrastructure, consistent maintenance routines, and community support networks.
+Ultimately, our results support the hypothesis that the benefits of backyard chicken keeping outweigh the challenges for most practitioners, though successful implementation depends on household-specific variables and community context.
+This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
+keywords: [chickens, backyard, eggs, homestead]
 author-note:

### 2025-03-01 Manuscript_Final.qmd
change name of title

@@
 ---
-title: "That-s-a-BigAss-Chicken"
-shorttitle: "Example apaquarto manuscript"
+title:“That’s a BigAss Chicken:  Care and Management of Large Chicken Breeds for Optimal Health and Productivity”
+shorttitle: " "That-s-a-BigAss-Chicken"
 author:

### 2025-03-01 Manuscript_Final.qmd
added stuff to YAML

--- 2025-03-01 Manuscript_Final.qmd
@@
       - name: The University of Chicago 
-        department: Division of the Social Sciences Psychology 
-        address: 5801 S Ellis Ave
+        department: Department of Psychology 
+        address: 5848 S. University Avenue
         city: Chicago
@@
         postal-code: 60637
+    role:
+      - methodology
+      - editing
   - name: Kristen M. Johnson
-    orcid: 
-    email: kvbecerra@Uchicago.edu 
+    orcid: 0009-0008-3757-5795
+    email: kmjohnson25@uchicago.edu 
     affiliations:
       - name: The University of Chicago 
-        department: Division of the Social Sciences Psychology 
-        address: 5801 S Ellis Ave
+        department: Department of Psychology 
+        address: 5848 S. University Avenue
         city: Chicago
@@
         postal-code: 60637
+    role:
+      - writing
+      - conceptualization
+- name: Michael Moroz
+    orcid: 
+    email:  mrmoroz@uchicago.edu
+    affiliations:
+      - name: The University of Chicago 
+        department: Department of Psychology 
+        address: 5848 S. University Avenue
+        city: Chicago
+        region: IL
+        country: USA
+        postal-code: 60637
+    role:
+      - formal anlaysis
+      - visualization
 
@@
 This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
-keywords: [chickens, backyard, eggs, homestead]
+keywords: [chickens, backyard, eggs, pros and cons]
 author-note:
   disclosures:
-    conflict of interest: The author has no conflict of interest to declare.
+    conflict of interest: The authors have no conflict of interest to declare.
 bibliography: # create a bib file in the root directory of your project

### 2025-03-01 Manuscript_Final.qmd
Completed data analysis (MM)

@@
 - name: Michael Moroz
-    orcid: 
+    orcid: 0009-0000-9772-0001
     email: mrmoroz@uchicago.edu
@@
 
+```{r data-analysis, echo=FALSE}
+
+#| label: data-analysis
+
+## Reading the data
+
+library(readr)
+
+chicken_data = read.csv("Data_BigAssChicken/ChickWeight.csv")
+
+# head(chicken_data)
+
+## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
+
+require(tidyverse)
+
+chicken_data = as_tibble(chicken_data)
+
+chicken_data = chicken_data %>%
+  select((-c(X)))
+
+head(chicken_data)
+
+## Changing the 'weight' column name to 'Weight' so everything remains consistent in terms of capitalization
+
+chicken_data = chicken_data %>%
+  rename(Weight = weight)
+
+## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))
+
+library(ggplot2)
+
+ggplot(chicken_data, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()
+
+## Ok now we have visualized the different growth trends of the various chickens.
+Now we probably want to look at how diet might factor into this trend.
+First let's calculate the mean growth rates of all the various chickens according to diet (rated 1 to 4)
+
+## Basic mathematical premise: end - start / start gives us the growth rate for a single period. Then we just add all the individual growth rates and divide by the number of periods
+
+chicken_data = chicken_data %>%
+  arrange(Chick, Time) %>%
+  group_by(Chick) %>%
+  mutate(GrowRate = (Weight - first(Weight)) / (Time - first(Time))) %>%
+  ungroup()
+
+## Now analyzing with diets
+
+dGrowRate = chicken_data %>%
+  group_by(Diet) %>%
+  summarise(meanGrowRate = mean(GrowRate, na.rm = TRUE))
+
+print(dGrowRate)
+
+## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.
+
+ggplot(dGrowRate, aes(x = Diet, y = meanGrowRate, fill = Diet)) + geom_bar(stat = "identity") + labs(x = "Diet", y = "Mean Growth Rate", title = "Figure 2: Mean Growth Rate Bar Plot (rate per day)") + theme_minimal()
+
+## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression.
+Let's try that now.
+
+lmWeight = lm(Weight ~ Time + Diet, data = chicken_data)
+summary(lmWeight)
+
+## So we see that both time and diet are significant predictors of weight.
+Meaning a one unit increase in time (which actually means going from 0 to 2, or 2 to 4, etc) corresponds with an 8.77 gram increase in weight.
+In addition, a one unit increase in diet (meaning going from diet 1 to 2, 2 to 3, or 3 to 4) corresponds with an 11.78 gram increase in weight.
+So the interpretation is that if using diet 4 as opposed to diet 1, you would see on average approximately a 33 gram weight increase.
+
+## Finally, plotting the regression
+
+ggplot(chicken_data, aes(x = Time, y = Weight, color = Diet, group = Diet)) + geom_point() + geom_smooth(method = "lm", se = FALSE) + labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet", title = "Figure 3: Regression of Weight on Time by Diet")
+
+```
+
 Chickens are pretty great [@elkhoraibiBackyardChickensUnited2014; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard].

### 2025-03-01 Manuscript_Final.qmd
Finished data analysis (MM)
corrected title format

@@
 ---
-title:“That’s a BigAss Chicken:  Care and Management of Large Chicken Breeds for Optimal Health and Productivity”
-shorttitle: " "That-s-a-BigAss-Chicken"
+title: "That’s a BigAss Chicken: Care and Managementof Large Chicken Breeds for Optimal Health and Productivity"
+shorttitle: "That-s-a-BigAss-Chicken"
 author:
@@
 
-## Finally, plotting the regression
+## Finally, plotting the regression.
 

### 2025-03-01 Manuscript_Final.qmd
continuing to work on Qmd, adding to YAML, rewriting intro, and starting to play with embedded images.

@@
 ---
-title: "That’s a BigAss Chicken: Care and Managementof Large Chicken Breeds for Optimal Health and Productivity"
-shorttitle: "That-s-a-BigAss-Chicken"
+title: "That’s a Big-Ass Chicken: Care and Management of Large Chicken Breeds for Optimal Health and Productivity"
+shorttitle: "That's a Big-Ass Chicken"
 author:
@@
     email: kvbecerra@Uchicago.edu 
+    corresponding: true
     affiliations:
@@
         postal-code: 60637
+        id: uchicago
     role:
+      - conceptualization
+      - formal anlaysis
       - methodology
+      - project administration
+      - software
+      - visualization
       - editing 
@@
     affiliations:
-      - name: The University of Chicago 
-        department: Department of Psychology 
-        address: 5848 S. University Avenue
-        city: Chicago
-        region: IL
-        country: USA
-        postal-code: 60637
+      - ref: uchicago
     role:
+      - conceptualization
+      - data curation
+      - methodology
+      - project administration
+      - software
       - writing
-      - conceptualization
+      - editing
   - name: Michael Moroz
@@
     affiliations:
-      - name: The University of Chicago 
-        department: Department of Psychology 
-        address: 5848 S. University Avenue
-        city: Chicago
-        region: IL
-        country: USA
-        postal-code: 60637
+      - ref: uchicago
     role:
       - formal anlaysis
+      - software
       - visualization
-
+      - editing
 abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices.
@@
     conflict of interest: The authors have no conflict of interest to declare.
-bibliography: # create a bib file in the root directory of your project
-format:
+  financial-support: "This study was supported by Grant from The International Society for Fowl Language."
+  gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
+impact-statement: "This study illustrates not only how, but also why one should raise big-ass backyard chickens.
+The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
+bibliography: That-s-a-BigAss-Chicken.bib
+floatsintext: true
+documentmode: man
+donotrepeattitle: true
+fontsize: 12pt
   #apaquarto-docx: default 
-  apaquarto-html: default    # remember to reverse commenting out other formats
-  apaquarto-pdf: default
+apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
+  #apaquarto-pdf: default
 ---
 
-```{r}
+```{r, echo=FALSE}
+
+# Where we will load all of the necessary libraries etc.
 
@@
 
-```{r data-analysis, echo=FALSE}
+> *If you've ever seen a picture of Eddy the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
+
+```{r}
+#![Eddy the Chicken](sampleimage.png){
+  #fig-myimportedimage 
+ # width="5in" 
+ # fig-alt="A picture of Eddy the Chicken being a Big-Ass Chicken on the shoulder of the first author's sister." 
+ # apa-note="This is a Big-Ass Chicken."
+ # }
+```
+
+In recent decades, the practice of maintaining domestic poultry within urban and suburban residential settings has experienced a notable resurgence [cite].
+This phenomenon, colloquially referred to as "backyard chicken keeping," represents a fascinating intersection of agricultural tradition and contemporary sustainability movements.
+The economic landscape has further accelerated this trend, as inflated egg prices have prompted an increasing number of households to consider domestic poultry as a pragmatic response to marketplace volatility [cite].
+Indeed, consumer data suggests that the correlation between rising commercial egg costs and the purchase of chicken coops is remarkably robust.
+
+[paragraph about why bigger is better, with regards to egg production and everything else]
+
+Previous studies have largely focused either on large-scale commercial poultry operations or on historical agricultural practices.
+While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution---a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate.
+Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the Big-Ass Chicken (BAC).
+This study aims to fill that obvious (and sizeable) gap.
+
+# Current Study
+Our research design employs a mixed methods approach to develop a nuanced understanding of this increasingly common practice.
+The methodology combines quantitative data analysis examining multiple factors related to Big-Ass backyard chicken husbandry---including analysis of factors related to chicken size and egg production---with qualitative thematic analysis of an in-depth interviews conducted with chicken owners of BAC's.
+By triangulating these methodological approaches, we aspire to move beyond anecdotal evidence and develop an empirically robust understanding of what might be termed the "net hennefit" of backyard chicken husbandry in contemporary urban contexts.
+The present study thus investigates the hypothesis that the benefits of maintaining a small flock of Gallus gallus domesticus (see Figure 2) in residential settings significantly outweigh the associated challenges and drawbacks.
+
+![Gallus gallus domesticus](orpington chicken.jfif){
+  #fig-orpington-chicken
+  width="5in" 
+  fig-alt="A picture of a common backyard chicken." 
+  apa-note="Also known as the orpinton chicken."
+  }
+
+# Method
+
+## Participants
+
+## Procedure
+
+## Measures
+
+# Results
+
+```{r, echo=FALSE}
 
@@
 
-Chickens are pretty great [@elkhoraibiBackyardChickensUnited2014; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard].
+# Discussion
 
-/clear
 # References

### 2025-03-01 Manuscript_Final.qmd
edits on manuscript...can't get it to do the correct formatting

@@
 This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
-keywords: [chickens, backyard, eggs, pros and cons]
+keywords: [chickens, backyard, eggs, pros and cons, bigger is better]
 author-note:
@@
 donotrepeattitle: true
+mainfont: "Times New Roman"
 fontsize: 12pt
   #apaquarto-docx: default 
-apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
-  #apaquarto-pdf: default
+ #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
+apaquarto-pdf: default
 ---
@@
 
-```{r}
+```{r, echo=FALSE}
 #![Eddy the Chicken](sampleimage.png){

### 2025-03-02 Manuscript_Final.qmd
correct name
edit hen name and photo

@@
 
-> *If you've ever seen a picture of Eddy the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
+> *If you've ever seen a picture of Edgar the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
 
 ```{r, echo=FALSE}
-#![Eddy the Chicken](sampleimage.png){
+#![Edgar the Chicken](orpignton hen(edgar).jpg){
   #fig-myimportedimage 

### 2025-03-02 Manuscript_Final.qmd
big chicken photo

--- 2025-03-01 Manuscript_Final.qmd
@@
 
-> *If you've ever seen a picture of Eddy the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
+> *If you've ever seen a picture of Pechugas the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
 
 ```{r, echo=FALSE}
-#![Eddy the Chicken](sampleimage.png){
+#![Edgar the Chicken](orpgton rooster.jpg){
   #fig-myimportedimage 

### 2025-03-03 Manuscript_Drafts.Rmd
story about chicken keeping

@@
 Current study 
+narratives of chicken keeping
+A day of taking care of chickens
+The day starts at around 7am for most of the group except for Edgar the chicken who has a later start to her morning.
+I own 5 chickens 3 roosters and 2 hens and they all have their own personalities and routines.
+Once everyone is up they are told good morning and given fresh water and food.
+Their breakfast consists of high protein grains and for the hens they are given a calcium supplement or layer pallets to help with egg production.
+After breakfast, the chickens are let out of their coop to roam around the yard.
+In my Georgia home we have about a football field worth of space for them to run around in .They are given a few hours to roam around and forage for bugs and other treats.During the colder months they are given mealworms for extra protein.They also have occasional fun treats such as blueberries, cucumbers and watermelon when in season.
+They are able to go in and out the coop to the run around the plot as they please.
+The
 Methods

### 2025-03-03 Manuscript_Final.qmd
library loading
testing chnages
If this doesn't workI am going to lose it...please do not delete or move any of this stuff

--- 2025-03-01 Manuscript_Final.qmd
@@
 ---
-title: "That’s a Big-Ass Chicken: Care and Management of Large Chicken Breeds for Optimal Health and Productivity"
+title: "That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry"
 shorttitle: "That's a Big-Ass Chicken"
@@
   - name: Karen Veronica Becerra
+    corresponding: true
     orcid: 0009-0006-4967-0955
     email: kvbecerra@Uchicago.edu 
-    corresponding: true
     affiliations:
@@
 abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices.
-Employing a mixed methods approach, we analyzed quantitative data from 157 participants across three metropolitan areas to assess economic factors, time investment, and regulatory compliance associated with domestic poultry husbandry.
+Employing a mixed methods approach, we analyzed quantitative data from ______.
 Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges.
@@
   disclosures:
-    conflict of interest: The authors have no conflict of interest to declare.
-  financial-support: "This study was supported by Grant from The International Society for Fowl Language."
+    conflict of interest: The authors have no conflicts of interest to declare.
+  financial-support: "This study was supported by a grant from The International Society for Fowl Language."
   gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
@@
 The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
-bibliography: That-s-a-BigAss-Chicken.bib
+bibliography: Chickens.bib
+format: 
+  #apaquarto-docx: default 
+  #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
+  apaquarto-pdf: default
 floatsintext: true
@@
 fontsize: 12pt
-  #apaquarto-docx: default 
- #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
-apaquarto-pdf: default
+
 ---
 
-```{r, echo=FALSE}
-
-# Where we will load all of the necessary libraries etc.
+```{r, echo=FALSE, include=FALSE}
+# Load necessary libraries
+library(readr)
+library(tidyverse)
+library(ggplot2)
 
@@
 
-> *If you've ever seen a picture of Eddy the Chicken, your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct. See Figure 1 for reference.*
+> *If you've ever seen a picture of Pechugas the Rooster (Fig. 1), your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct.*
 
-```{r, echo=FALSE}
-#![Eddy the Chicken](sampleimage.png){
+![Pechugas the Rooster](Images_BigAssChicken/orpignton rooster.jpg){
   #fig-myimportedimage 
- # width="5in" 
- # fig-alt="A picture of Eddy the Chicken being a Big-Ass Chicken on the shoulder of the first author's sister." 
- # apa-note="This is a Big-Ass Chicken."
- # }
-```
+  width="4in" 
+  fig-alt="A picture of Pechugas the Rooster being a Big-Ass Chicken." 
+  apa-note="This is a Big-Ass Chicken."
+  }
 
-In recent decades, the practice of maintaining domestic poultry within urban and suburban residential settings has experienced a notable resurgence [cite].
+In recent decades, the practice of maintaining domestic poultry within urban and suburban residential settings has experienced a notable resurgence [@maceBackyardOurBeds2024].
 This phenomenon, colloquially referred to as "backyard chicken keeping," represents a fascinating intersection of agricultural tradition and contemporary sustainability movements.
-The economic landscape has further accelerated this trend, as inflated egg prices have prompted an increasing number of households to consider domestic poultry as a pragmatic response to marketplace volatility [cite].
-Indeed, consumer data suggests that the correlation between rising commercial egg costs and the purchase of chicken coops is remarkably robust.
+The economic landscape has further accelerated this trend, as inflated egg prices have prompted an increasing number of households to consider domestic poultry as a pragmatic response to marketplace volatility [@italieSoaringEggPrices2025].
+Indeed, consumer data suggests that the correlation between rising commercial egg costs and the purchase of chicken coops is remarkably robust[@kagayaPriceAttentionAnalysis2025].
 
@@
 
-Previous studies have largely focused either on large-scale commercial poultry operations or on historical agricultural practices.
+Previous studies have largely focused either on large-scale commercial poultry operations or on historical agricultural practices [@bistSustainablePoultryFarming2024; @grzinicIntensivePoultryFarming2023; @jeniOverviewHealthChallenges2021].
 While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution---a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate.
-Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the Big-Ass Chicken (BAC).
+Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the Big-Ass Chicken (BAC)[@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022].
 This study aims to fill that obvious (and sizeable) gap.
@@
 Our research design employs a mixed methods approach to develop a nuanced understanding of this increasingly common practice.
-The methodology combines quantitative data analysis examining multiple factors related to Big-Ass backyard chicken husbandry---including analysis of factors related to chicken size and egg production---with qualitative thematic analysis of an in-depth interviews conducted with chicken owners of BAC's.
+The methodology combines quantitative data analysis examining multiple factors related to Big-Ass backyard chicken husbandry---including analysis of factors related to chicken size and egg production---with qualitative thematic analysis of in-depth interviews conducted with chicken owners of BAC's.
 By triangulating these methodological approaches, we aspire to move beyond anecdotal evidence and develop an empirically robust understanding of what might be termed the "net hennefit" of backyard chicken husbandry in contemporary urban contexts.
-The present study thus investigates the hypothesis that the benefits of maintaining a small flock of Gallus gallus domesticus (see Figure 2) in residential settings significantly outweigh the associated challenges and drawbacks.
+The present study thus investigates two hypotheses:
+1. The benefits of maintaining a small flock of Gallus gallus domesticus (see Figure 2) in residential settings significantly outweigh the associated challenges and drawbacks.
+2. Raising BAC's will result in an increased number of perceived benefits relative to drawbacks.
 
-![Gallus gallus domesticus](orpington chicken.jfif){
+![Gallus gallus domesticus](Images_BigAssChicken/Orpignton hen(edgar).jpg){
   #fig-orpington-chicken
-  width="5in" 
+  width="4in" 
   fig-alt="A picture of a common backyard chicken." 
-  apa-note="Also known as the orpinton chicken."
+  apa-note="Also known as the Orpington chicken."
   }
@@
 # Method
+## Participants
+### Chickens
+We looked at 50 Gallus gallus domesticus chicks, starting from hatching...
 
-## Participants
+### Humans
+We looked at interview of ___ individuals from ___
 
 ## Procedure
+### Quantitative
+We measured the weight of chickens ....
+
+### Qualitative
+We conducted thematic analysis of transcripts from recorded in depth interviews with owners of backyard chickens, including BAC's.
 
 ## Measures
+### Quantitative
+
+### Qualitative
+thematic analysis
 
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, include=FALSE}
 
@@
 ## Reading the data 
-
-library(readr)
-
-chicken_data = read.csv("Data_BigAssChicken/ChickWeight.csv")
+chicken_weight = read.csv("Data_BigAssChicken/ChickWeight.csv")
 
 # head(chicken_data)
+## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
+chicken_weight = as_tibble(chicken_weight)
 
-## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
-
-require(tidyverse)
-
-chicken_data = as_tibble(chicken_data)
-
-chicken_data = chicken_data %>%
+chicken_weight = chicken_weight %>%
   select((-c(X)))
 
-head(chicken_data)
+head(chicken_weight)
 
 ## Changing the 'weight' column name to 'Weight' so everything remains consistent in terms of capitalization
+chicken_weight = chicken_weight %>%
+  rename(Weight = weight)
+```
 
-chicken_data = chicken_data %>%
-  rename(Weight = weight)
-
+```{r, echo=FALSE}
 ## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))
 
-library(ggplot2)
+ggplot(chicken_weight, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()
 
-ggplot(chicken_data, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()
+```
 
+```{r, echo=FALSE, include=FALSE}
 ## Ok now we have visualized the different growth trends of the various chickens.
@@
 
-chicken_data = chicken_data %>%
+chicken_weight = chicken_weight %>%
   arrange(Chick, Time) %>%
@@
 
-dGrowRate = chicken_data %>%
+dGrowRate = chicken_weight %>%
   group_by(Diet) %>%
@@
 print(dGrowRate)
+```
 
+```{r, echo=FALSE}
 ## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.
@@
 
+```
+
+```{r, echo=FALSE, include=FALSE}
 ## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression.
@@
 
-lmWeight = lm(Weight ~ Time + Diet, data = chicken_data)
+lmWeight = lm(Weight ~ Time + Diet, data = chicken_weight)
 summary(lmWeight)
@@
 
+```
+
+```{r}
+#| echo: FALSE
+#| label: regression-plot
+#| fig-cap: Regression of Weight on Time by Diet
+
 ## Finally, plotting the regression.
-
-ggplot(chicken_data, aes(x = Time, y = Weight, color = Diet, group = Diet)) + geom_point() + geom_smooth(method = "lm", se = FALSE) + labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet", title = "Figure 3: Regression of Weight on Time by Diet")
+ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE) + 
+  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
 

### 2025-03-04 BAC_Qualitative-Data.Rmd
added all the qualitative stuff (maybe went overboard in imagining owning chickens)

---
title: "BAC_Qualitative-Data"
author: "Kristen Johnson"
date: "2025-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# [MADE UP] QUALITATIVE DATA: Thematic Analysis of Interviews with Urban Backyard Chicken Farmers

## Methodology

Semi-structured interviews were conducted with 50 urban backyard chicken keepers (32 female, 17 male, 1 non-binary) across three metropolitan areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15). Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = 3.7 years). Flock sizes ranged from 2-15 birds (median = 4). Interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis. Initial coding was conducted independently by two researchers, followed by collaborative theme development. Member-checking was employed with a subset of 12 participants to verify thematic authenticity.

## Themes and Subthemes

### 1. Economic Pragmatism

#### 1.1 Response to Market Volatility
Participants frequently cited economic considerations as initial motivations for chicken keeping, with 38 participants (76%) specifically mentioning rising egg prices:

> "When eggs hit seven dollars a dozen last winter, that was my tipping point. I did the math and realized a coop would pay for itself within a year." (Participant 23, Midwest)

#### 1.2 Beyond Simple Cost Calculations
While economic benefits served as initial motivations, participants described a more complex value proposition that extended beyond mere cost savings:

> "It's not just about saving money on eggs anymore. There's value in knowing exactly what my birds are eating, how they're treated, and connecting with my food source." (Participant 7, Eastern Seaboard)

#### 1.3 Unexpected Economic Benefits
Many participants (n=29, 58%) reported unanticipated economic advantages, including reduced food waste, garden fertilization, and pest control:

> "They eat all our kitchen scraps, turn them into eggs and fantastic compost. My garden has never been more productive, which means even more grocery savings." (Participant 42, Pacific Northwest)

### 2. Self-Sufficiency and Food Security

#### 2.1 Control Over Food Supply
A dominant theme emerged around increased feelings of food security and self-reliance:

> "After supply chain disruptions during COVID, having my own egg supply feels like insurance. No matter what happens at the grocery store, we've got breakfast." (Participant 11, Eastern Seaboard)

#### 2.2 Quality and Freshness
Nearly all participants (n=47, 94%) emphasized superior egg quality as a significant benefit:

> "Store-bought eggs are a completely different food. Once you've had eggs with those vibrant orange yolks from your backyard, there's no comparison." (Participant 39, Pacific Northwest)

#### 2.3 Stepping Stone to Greater Self-Reliance
Many participants (n=31, 62%) described chicken keeping as part of a broader trajectory toward increased self-sufficiency:

> "The chickens were our gateway. Now we've got vegetable beds, rainwater collection, and we're thinking about beekeeping next year." (Participant 28, Midwest)

### 3. Social and Community Dimensions

#### 3.1 Neighborhood Connections
Unexpectedly, chicken keeping frequently facilitated community building:

> "Our chickens are neighborhood celebrities. Kids stop by after school, neighbors trade garden produce for eggs, and we've met people on our street we never spoke to before." (Participant 3, Eastern Seaboard)

#### 3.2 Educational Value
Families with children (n=22) universally cited educational benefits:

> "My kids understand where food comes from. They've witnessed the whole life cycle, learned responsibility through daily care, and developed empathy for animals." (Participant 45, Pacific Northwest)

#### 3.3 Negotiating Regulations and Relationships
Navigating municipal regulations and neighbor relationships emerged as significant challenges:

> "Getting the permit was straightforward, but keeping peace with one particular neighbor has been ongoing diplomacy. Giving them free eggs helps." (Participant 19, Midwest)

### 4. Practical Challenges and Adaptations

#### 4.1 Time Commitment Reality
Time requirements emerged as the most frequently cited challenge (n=41, 82%):

> "The daily care is minimal, maybe 10 minutes. But when something goes wrong—a predator gets in, or a bird gets sick—suddenly it's very time-intensive." (Participant 34, Pacific Northwest)

#### 4.2 Seasonal Variability
Participants described adapting to natural laying cycles:

> "Winter egg production drops dramatically. You either accept buying eggs for a few months or install coop lighting, which raises ethical questions about manipulating their natural cycles." (Participant 8, Eastern Seaboard)

#### 4.3 Learning Curve and Resource Networks
Most participants (n=43, 86%) described a significant learning curve, mitigated by online communities:

> "YouTube and Facebook groups were lifesavers. There's always someone online who's dealt with whatever weird chicken situation you're facing at 11 PM." (Participant 14, Midwest)

### 5. Psychological and Emotional Benefits

#### 5.1 Stress Reduction
An unexpected theme emerged around the stress-reducing properties of chicken keeping:

> "Watching the chickens scratch and peck is meditative. After a stressful workday, I'll sit with a cup of tea and just observe them. Better than therapy." (Participant 31, Midwest)

#### 5.2 Connection to Agricultural Heritage
Many participants (n=26, 52%) described chicken keeping as connecting them to family heritage:

> "My grandmother kept chickens. When I collect eggs, I feel connected to her and generations of women in my family who did this same simple act." (Participant 5, Eastern Seaboard)

#### 5.3 Identity and Values Alignment
Chicken keeping frequently represented an expression of environmental and ethical values:

> "It's living my values around humane animal treatment, reducing my carbon footprint, and stepping outside the industrial food system, even if in a small way." (Participant 47, Pacific Northwest)

## Intersection of Themes

The interrelationship between themes reveals that while economic considerations often initiated chicken keeping, sustained practice was motivated by a complex interplay of factors. Particularly notable was the transformation from primarily economic motivation to deeper psychological, social, and philosophical benefits over time. As one participant summarized:

> "We started for the eggs, but we continue for everything else—the compost, the joy they bring to our kids, the neighbors they've introduced us to, and the simple pleasure of caring for animals that provide for us in return." (Participant 17, Midwest)

## Conclusion

This thematic analysis reveals backyard chicken keeping as a multidimensional practice extending well beyond utilitarian egg production. The initial economic calculus frequently evolves into a complex set of values-based, social, and psychological benefits that practitioners find equally or more compelling than the original financial motivation. Challenges are acknowledged but generally framed as manageable through adaptation, learning, and community support. These findings support our quantitative results indicating that practitioners perceive the benefits of backyard chicken keeping to outweigh the associated challenges, though with important nuance regarding the evolving nature of what constitutes "benefit" over the course of the practice.

### 2025-03-04 Manuscript_Final.qmd
added all the qualitative stuff (maybe went overboard in imagining owning chickens)

@@
 ```{r, echo=FALSE, include=FALSE}
+
 # Load necessary libraries
@@
 library(ggplot2)
+library(tidyverse)
+library(flextable)
 
@@
 ### Humans
-We looked at interview of ___ individuals from ___
+Semi-structured interviews were conducted with 50 urban backyard chicken keepers (32 female, 17 male, 1 non-binary) across three metropolitan areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15).
+Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = 3.7 years).
+Flock sizes ranged from 2-15 birds (median = 4).
 
@@
 ### Qualitative
-We conducted thematic analysis of transcripts from recorded in depth interviews with owners of backyard chickens, including BAC's.
+Semi-structured interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis.
+Initial coding was conducted independently by two researchers, followed by collaborative theme development.
+Member-checking was employed with a subset of 12 participants to verify thematic authenticity.
 
@@
 # Results
-
+## Chickens  
 ```{r, echo=FALSE, include=FALSE}
@@
 
+## Eggs
+
+## Owners: Qualitative Themes and Subthemes 
+Thematic Analysis of the transcribed interviews revealed five major themes: Economic Pragmatism, Self-Sufficiency and Food Security, Social and Community Dimensions, Practical Challenges and Adaptations, and Psychological and Emotional Benefits.
+
+### 1. Economic Pragmatism
+
+#### 1.1 Response to Market Volatility
+Participants frequently cited economic considerations as initial motivations for chicken keeping, with 38 participants (76%) specifically mentioning rising egg prices:
+
+> "When eggs hit seven dollars a dozen last winter, that was my tipping point. I did the math and realized a coop would pay for itself within a year." (Participant 23, Midwest)
+
+> "My Jersey Giants [BACs] lay fewer eggs than production breeds, but each egg is nearly twice the size.
+One of my BAC eggs equals two store-bought large eggs in recipes, so the economics actually work out better for my family of five." (Participant 4, Eastern Seaboard, BAC owner)
+
+#### 1.2 Beyond Simple Cost Calculations
+While economic benefits served as initial motivations, participants described a more complex value proposition that extended beyond mere cost savings:
+
+> "It's not just about saving money on eggs anymore.
+There's value in knowing exactly what my birds are eating, how they're treated, and connecting with my food source." (Participant 7, Eastern Seaboard)
+
+#### 1.3 Unexpected Economic Benefits
+Many participants (n=29, 58%) reported unanticipated economic advantages, including reduced food waste, garden fertilization, and pest control:
+
+> "They eat all our kitchen scraps, turn them into eggs and fantastic compost. My garden has never been more productive, which means even more grocery savings." (Participant 42, Pacific Northwest)
+
+### 2. Self-Sufficiency and Food Security
+
+#### 2.1 Control Over Food Supply
+A dominant theme emerged around increased feelings of food security and self-reliance:
+
+> "After supply chain disruptions during COVID, having my own egg supply feels like insurance. No matter what happens at the grocery store, we've got breakfast." (Participant 11, Eastern Seaboard)
+
+> "My Brahmas [BACs] aren't just egg layers—they're dual-purpose birds.
+In a true food security crisis, each bird represents about 10 pounds of meat.
+I don't plan to eat them, but there's peace of mind knowing these massive birds could feed my family for weeks if necessary." (Participant 29, Midwest, BAC owner)
+
+#### 2.2 Quality and Freshness
+Nearly all participants (n=47, 94%) emphasized superior egg quality as a significant benefit:
+
+> "Store-bought eggs are a completely different food. Once you've had eggs with those vibrant orange yolks from your backyard, there's no comparison." (Participant 39, Pacific Northwest)
+
+#### 2.3 Stepping Stone to Greater Self-Reliance
+Many participants (n=31, 62%) described chicken keeping as part of a broader trajectory toward increased self-sufficiency:
+
+> "The chickens were our gateway. Now we've got vegetable beds, rainwater collection, and we're thinking about beekeeping next year." (Participant 28, Midwest)
+
+### 3. Social and Community Dimensions
+
+#### 3.1 Neighborhood Connections
+Unexpectedly, chicken keeping frequently facilitated community building:
+
+> "Our chickens are neighborhood celebrities.
+Kids stop by after school, neighbors trade garden produce for eggs, and we've met people on our street we never spoke to before." (Participant 3, Eastern Seaboard)
+
+> "My Cochin giants [BACs] are absolute neighborhood attractions.
+People literally schedule visits to see these fluffy behemoths.
+I've started hosting monthly 'Big-Ass Chicken Socials' where neighbors bring drinks and appetizers just to hang out with these gentle giants.
+They've become community mascots." (Participant 36, Pacific Northwest, BAC owner)
+
+#### 3.2 Educational Value
+Families with children (n=22) universally cited educational benefits:
+
+> "My kids understand where food comes from. They've witnessed the whole life cycle, learned responsibility through daily care, and developed empathy for animals." (Participant 45, Pacific Northwest)
+
+#### 3.3 Negotiating Regulations and Relationships
+Navigating municipal regulations and neighbor relationships emerged as significant challenges:
+
+> "Getting the permit was straightforward, but keeping peace with one particular neighbor has been ongoing diplomacy. Giving them free eggs helps." (Participant 19, Midwest)
+
+### 4. Practical Challenges and Adaptations
+
+#### 4.1 Time Commitment Reality
+Time requirements emerged as the most frequently cited challenge (n=41, 82%):
+
+> "The daily care is minimal, maybe 10 minutes. But when something goes wrong—a predator gets in, or a bird gets sick—suddenly it's very time-intensive." (Participant 34, Pacific Northwest)
+
+> "Keeping BACs requires special planning.
+My Orpingtons eat nearly twice what standard birds consume, and their massive droppings mean more frequent coop cleaning.
+The flip side is that predators leave them completely alone—even neighborhood dogs keep their distance from these 12-pound behemoths.
+No raccoon is brave enough to take on my roosters." (Participant 12, Eastern Seaboard, BAC owner)
+
+#### 4.2 Seasonal Variability
+Participants described adapting to natural laying cycles:
+
+> "Winter egg production drops dramatically.
+You either accept buying eggs for a few months or install coop lighting, which raises ethical questions about manipulating their natural cycles." (Participant 8, Eastern Seaboard)
+
+#### 4.3 Learning Curve and Resource Networks
+Most participants (n=43, 86%) described a significant learning curve, mitigated by online communities:
+
+> "YouTube and Facebook groups were lifesavers. There's always someone online who's dealt with whatever weird chicken situation you're facing at 11 PM." (Participant 14, Midwest)
+
+### 5. Psychological and Emotional Benefits
+
+#### 5.1 Stress Reduction
+An unexpected theme emerged around the stress-reducing properties of chicken keeping:
+
+> "Watching the chickens scratch and peck is meditative. After a stressful workday, I'll sit with a cup of tea and just observe them. Better than therapy." (Participant 31, Midwest)
+
+> "There's something profoundly calming about my Australorps [BACs].
+Their size makes them move more slowly and deliberately than smaller breeds.
+My blood pressure literally drops when I'm with them.
+After my heart attack, my cardiologist actually wrote 'BAC therapy' into my recovery plan—jokingly, but I take it seriously.
+Spending time with these gentle giants is legitimately therapeutic." (Participant 25, Midwest, BAC owner)
+
+#### 5.2 Connection to Agricultural Heritage
+Many participants (n=26, 52%) described chicken keeping as connecting them to family heritage:
+
+> "My grandmother kept chickens. When I collect eggs, I feel connected to her and generations of women in my family who did this same simple act." (Participant 5, Eastern Seaboard)
+
+#### 5.3 Identity and Values Alignment
+Chicken keeping frequently represented an expression of environmental and ethical values:
+
+> "It's living my values around humane animal treatment, reducing my carbon footprint, and stepping outside the industrial food system, even if in a small way." (Participant 47, Pacific Northwest)
+
+```
 # Discussion

### 2025-03-05 BAC_Manuscript_Drafts.Rmd
moved and renamed files

--- 2025-03-03 Manuscript_Drafts.Rmd
@@
 The findings will contribute to the broader discourse on sustainable animal husbandry and inform best practices for individuals seeking to maintain healthy, productive backyard flocks.
-Abstract
-Introduction 
-Current study 
-narratives of chicken keeping
+
+# narratives of chicken keeping
 A day of taking care of chickens
@@
 The
+
 Methods
+
 Results 

### 2025-03-05 Data_BigAssChicken/BAC_Qualitative-Data.Rmd
moved and renamed files

--- 2025-03-04 BAC_Qualitative-Data.Rmd
@@
 # [MADE UP] QUALITATIVE DATA: Thematic Analysis of Interviews with Urban Backyard Chicken Farmers
+
+## Methodology
+
+Semi-structured interviews were conducted with 50 urban backyard chicken keepers (32 female, 17 male, 1 non-binary) across three metropolitan areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15).
+Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = 3.7 years).
+Flock sizes ranged from 2-15 birds (median = 4).
+Interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis.
+Initial coding was conducted independently by two researchers, followed by collaborative theme development.
+Member-checking was employed with a subset of 12 participants to verify thematic authenticity.
+
+## Themes and Subthemes
+
+### 1. Economic Pragmatism
+
+#### 1.1 Response to Market Volatility
+Participants frequently cited economic considerations as initial motivations for chicken keeping, with 38 participants (76%) specifically mentioning rising egg prices:
+
+> "When eggs hit seven dollars a dozen last winter, that was my tipping point. I did the math and realized a coop would pay for itself within a year." (Participant 23, Midwest)
+
+> "My Jersey Giants [BACs] lay fewer eggs than production breeds, but each egg is nearly twice the size.
+One of my BAC eggs equals two store-bought large eggs in recipes, so the economics actually work out better for my family of five." (Participant 4, Eastern Seaboard, BAC owner)
+
+#### 1.2 Beyond Simple Cost Calculations
+While economic benefits served as initial motivations, participants described a more complex value proposition that extended beyond mere cost savings:
+
+> "It's not just about saving money on eggs anymore.
+There's value in knowing exactly what my birds are eating, how they're treated, and connecting with my food source." (Participant 7, Eastern Seaboard)
+
+#### 1.3 Unexpected Economic Benefits
+Many participants (n=29, 58%) reported unanticipated economic advantages, including reduced food waste, garden fertilization, and pest control:
+
+> "They eat all our kitchen scraps, turn them into eggs and fantastic compost. My garden has never been more productive, which means even more grocery savings." (Participant 42, Pacific Northwest)
+
+### 2. Self-Sufficiency and Food Security
+
+#### 2.1 Control Over Food Supply
+A dominant theme emerged around increased feelings of food security and self-reliance:
+
+> "After supply chain disruptions during COVID, having my own egg supply feels like insurance. No matter what happens at the grocery store, we've got breakfast." (Participant 11, Eastern Seaboard)
+
+> "My Brahmas [BACs] aren't just egg layers—they're dual-purpose birds.
+In a true food security crisis, each bird represents about 10 pounds of meat.
+I don't plan to eat them, but there's peace of mind knowing these massive birds could feed my family for weeks if necessary." (Participant 29, Midwest, BAC owner)
+
+#### 2.2 Quality and Freshness
+Nearly all participants (n=47, 94%) emphasized superior egg quality as a significant benefit:
+
+> "Store-bought eggs are a completely different food. Once you've had eggs with those vibrant orange yolks from your backyard, there's no comparison." (Participant 39, Pacific Northwest)
+
+#### 2.3 Stepping Stone to Greater Self-Reliance
+Many participants (n=31, 62%) described chicken keeping as part of a broader trajectory toward increased self-sufficiency:
+
+> "The chickens were our gateway. Now we've got vegetable beds, rainwater collection, and we're thinking about beekeeping next year." (Participant 28, Midwest)
+
+### 3. Social and Community Dimensions
+
+#### 3.1 Neighborhood Connections
+Unexpectedly, chicken keeping frequently facilitated community building:
+
+> "Our chickens are neighborhood celebrities.
+Kids stop by after school, neighbors trade garden produce for eggs, and we've met people on our street we never spoke to before." (Participant 3, Eastern Seaboard)
+
+> "My Cochin giants [BACs] are absolute neighborhood attractions.
+People literally schedule visits to see these fluffy behemoths.
+I've started hosting monthly 'Big-Ass Chicken Socials' where neighbors bring drinks and appetizers just to hang out with these gentle giants.
+They've become community mascots." (Participant 36, Pacific Northwest, BAC owner)
+
+#### 3.2 Educational Value
+Families with children (n=22) universally cited educational benefits:
+
+> "My kids understand where food comes from. They've witnessed the whole life cycle, learned responsibility through daily care, and developed empathy for animals." (Participant 45, Pacific Northwest)
+
+#### 3.3 Negotiating Regulations and Relationships
+Navigating municipal regulations and neighbor relationships emerged as significant challenges:
+
+> "Getting the permit was straightforward, but keeping peace with one particular neighbor has been ongoing diplomacy. Giving them free eggs helps." (Participant 19, Midwest)
+
+### 4. Practical Challenges and Adaptations
+
+#### 4.1 Time Commitment Reality
+Time requirements emerged as the most frequently cited challenge (n=41, 82%):
+
+> "The daily care is minimal, maybe 10 minutes. But when something goes wrong—a predator gets in, or a bird gets sick—suddenly it's very time-intensive." (Participant 34, Pacific Northwest)
+
+> "Keeping BACs requires special planning.
+My Orpingtons eat nearly twice what standard birds consume, and their massive droppings mean more frequent coop cleaning.
+The flip side is that predators leave them completely alone—even neighborhood dogs keep their distance from these 12-pound behemoths.
+No raccoon is brave enough to take on my roosters." (Participant 12, Eastern Seaboard, BAC owner)
+
+#### 4.2 Seasonal Variability
+Participants described adapting to natural laying cycles:
+
+> "Winter egg production drops dramatically.
+You either accept buying eggs for a few months or install coop lighting, which raises ethical questions about manipulating their natural cycles." (Participant 8, Eastern Seaboard)
+
+#### 4.3 Learning Curve and Resource Networks
+Most participants (n=43, 86%) described a significant learning curve, mitigated by online communities:
+
+> "YouTube and Facebook groups were lifesavers. There's always someone online who's dealt with whatever weird chicken situation you're facing at 11 PM." (Participant 14, Midwest)
+
+### 5. Psychological and Emotional Benefits
+
+#### 5.1 Stress Reduction
+An unexpected theme emerged around the stress-reducing properties of chicken keeping:
+
+> "Watching the chickens scratch and peck is meditative. After a stressful workday, I'll sit with a cup of tea and just observe them. Better than therapy." (Participant 31, Midwest)
+
+> "There's something profoundly calming about my Australorps [BACs].
+Their size makes them move more slowly and deliberately than smaller breeds.
+My blood pressure literally drops when I'm with them.
+After my heart attack, my cardiologist actually wrote 'BAC therapy' into my recovery plan—jokingly, but I take it seriously.
+Spending time with these gentle giants is legitimately therapeutic." (Participant 25, Midwest, BAC owner)
+
+#### 5.2 Connection to Agricultural Heritage
+Many participants (n=26, 52%) described chicken keeping as connecting them to family heritage:
+
+> "My grandmother kept chickens. When I collect eggs, I feel connected to her and generations of women in my family who did this same simple act." (Participant 5, Eastern Seaboard)
+
+#### 5.3 Identity and Values Alignment
+Chicken keeping frequently represented an expression of environmental and ethical values:
+
+> "It's living my values around humane animal treatment, reducing my carbon footprint, and stepping outside the industrial food system, even if in a small way." (Participant 47, Pacific Northwest)
+
+## Intersection of Themes
+
+The interrelationship between themes reveals that while economic considerations often initiated chicken keeping, sustained practice was motivated by a complex interplay of factors.
+Particularly notable was the transformation from primarily economic motivation to deeper psychological, social, and philosophical benefits over time.
+As one participant summarized:
+
+> "We started for the eggs, but we continue for everything else—the compost, the joy they bring to our kids, the neighbors they've introduced us to, and the simple pleasure of caring for animals that provide for us in return." (Participant 17, Midwest)
+
+## Conclusion
+
+This thematic analysis reveals backyard chicken keeping as a multidimensional practice extending well beyond utilitarian egg production.
+The initial economic calculus frequently evolves into a complex set of values-based, social, and psychological benefits that practitioners find equally or more compelling than the original financial motivation.
+Challenges are acknowledged but generally framed as manageable through adaptation, learning, and community support.
+These findings support our quantitative results indicating that practitioners perceive the benefits of backyard chicken keeping to outweigh the associated challenges, though with important nuance regarding the evolving nature of what constitutes "benefit" over the course of the practice.
+
+--------------------
 

### 2025-03-05 Manuscript_Final.qmd
not sure
added disscussion to qmd

--- 2025-03-02 Manuscript_Final.qmd
@@
 ```{r, echo=FALSE}
-
-# Where we will load all of the necessary libraries etc.
+# Load necessary libraries
+library(readr)
+library(tidyverse)
+library(ggplot2)
 
@@
 # Discussion
+The findings of this study underscore the economic, environmental, and social benefits of backyard chicken keeping while also highlighting the practical challenges that accompany this practice.
+Our results provide empirical support for the growing movement toward urban and suburban poultry husbandry, illustrating how households recover their initial investments and experience broader benefits related to sustainability and well-being.
+
+### Economic Considerations
+
+One of the most compelling findings is the financial feasibility of backyard chicken keeping.
+Despite an initial setup cost averaging $487, most participants reported recouping their investments within 14 months through egg production and additional savings in food waste reduction and garden fertilization.
+This aligns with previous research on urban agriculture, which emphasizes self-sufficiency and cost savings as key motivators [@maceBackyardOurBeds2024].
+Notably, owners of Big-Ass Chickens (BACs) described a cost-benefit ratio due to the larger egg sizes and increased meat yield potential.
+
+The study also highlights how economic motivations evolve over time.
+While rising commercial egg prices may initially drive adoption, many owners ultimately find additional value in food security, ethical treatment of animals, and sustainability.
+These findings suggest that policymakers and sustainability advocates could leverage economic incentives to promote backyard chicken keeping as a viable food security measure, particularly in urban settings.
+
+### Environmental and Sustainability Benefits
+
+In addition to economic advantages, backyard chicken keeping contributes to environmental sustainability by reducing food waste and enhancing soil quality.
+Participants widely reported using chickens to process kitchen scraps, turning waste into high-quality compost that improved garden productivity.
+This finding complements existing literature on the role of urban agriculture in sustainable food systems [@grzinicIntensivePoultryFarming2023].
+
+The contribution of this study is the exploration of BACs in sustainability efforts.
+Owners of larger breeds emphasized their birds' dual-purpose roles, noting their ability to provide both eggs and meat.
+Furthermore, their robust size and temperament reportedly made them more resistant to predation, reducing flock losses.
+Future research could examine how breed selection influences long-term sustainability outcomes in urban poultry keeping.
+
+### Social and Psychological Benefits
+
+Beyond economic and environmental factors, this study reveals the significant social and emotional benefits associated with backyard chicken keeping.
+Many participants reported stronger neighborhood connections facilitated by chicken ownership, with some even organizing community events centered around their flocks.
+This aligns with prior research on urban agriculture’s role in fostering social cohesion [@singhBackyardPoultryFarming2022]
+
+Psychologically, many owners described their chickens as sources of emotional support, with several likening them to pets.
+Participants noted stress reduction, increased outdoor activity, and a sense of accomplishment in maintaining their flocks.
+These findings suggest that backyard chicken keeping may serve as a form of therapeutic engagement, particularly for individuals seeking greater interaction with nature.
+
+###Practical Challenges and Considerations
+
+Despite the numerous benefits, backyard chicken keeping is not without challenges.
+Time commitment emerged as a key issue, with participants spending an average of 28 minutes per day on maintenance tasks.
+While many found the routine manageable, unexpected events such as illness, predation, or extreme weather—could significantly increase time demands.
+
+Navigating municipal regulations also posed a notable challenge.
+Many participants encountered restrictions on flock size, coop placement, and noise levels, requiring negotiation with local authorities and neighbors.
+These findings highlight the need for clear and accessible regulatory guidelines to support responsible backyard chicken keeping.
+
+Seasonal variations in productivity were another important consideration.
+Egg production naturally fluctuates based on daylight hours and molting cycles, requiring owners to plan accordingly.
+Some participants mitigated these challenges by supplementing light exposure or adjusting flock composition to include breeds with higher winter laying rates.
+
+## Conclusion
+
+This  study supports the hypothesis that the benefits of backyard chicken keeping outweigh the challenges.
+However, success depends on household-specific variables, including available space, time commitment, and municipal regulations.
+The inclusion of BACs as a focal point of this study provides unique insights into breed selection and its implications for economic and sustainability outcomes.
+
+Future research should further explore the long-term impacts of backyard chicken keeping on food security, community engagement, and mental health.
+Additionally, policymakers should consider strategies to facilitate responsible poultry keeping through supportive legislation and educational resources.
+By addressing these factors, backyard chicken keeping can continue to grow as a viable and sustainable practice in urban and suburban communities.
 

### 2025-03-05 Manuscript_Final.qmd
chaged bib

@@
 The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
-bibliography: That-s-a-BigAss-Chicken.bib
+bibliography: Chickens.bib
 floatsintext: true

### 2025-03-05 BAC_Manuscript_Final.qmd
chages and organizing of repo

---
title: "That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry"
shorttitle: "That's a Big-Ass Chicken"
author:
  - name: Karen Veronica Becerra
    corresponding: true
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Department of Psychology 
        address: 5848 S. University Avenue
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
        id: uchicago
    role:
      - conceptualization
      - formal anlaysis
      - methodology
      - project administration
      - software
      - visualization
      - editing 
  - name: Kristen M. Johnson
    orcid: 0009-0008-3757-5795
    email: kmjohnson25@uchicago.edu 
    affiliations:
      - ref: uchicago
    role:
      - conceptualization
      - data curation
      - methodology
      - project administration
      - software
      - writing
      - editing
  - name: Michael Moroz
    orcid: 0009-0000-9772-0001
    email: mrmoroz@uchicago.edu
    affiliations:
      - ref: uchicago
    role:
      - formal anlaysis
      - software
      - visualization
      - editing
abstract: "This study investigates the growing phenomenon of backyard chicken keeping in urban and suburban environments, a practice that has gained significant momentum amid rising commercial egg prices. Employing a mixed methods approach, we analyzed quantitative data from ______. Concurrently, we conducted thematic analysis of in-depth interviews with backyard chicken owners to explore perceived benefits and challenges. Our findings indicate that while initial setup costs average $487, households recover this investment within 14 months through egg production, with additional benefits including reduced food waste, improved garden soil quality, and reported increases in household well-being. Challenges identified include time commitment (averaging 28 minutes daily), navigating municipal regulations, and managing seasonal variations in productivity. Factor analysis revealed that success factors cluster around three dimensions: appropriate infrastructure, consistent maintenance routines, and community support networks. Ultimately, our results support the hypothesis that the benefits of backyard chicken keeping outweigh the challenges for most practitioners, though successful implementation depends on household-specific variables and community context. This research contributes to growing literature on urban agriculture while providing practical insights for potential chicken keepers, municipal policymakers, and sustainability advocates."
keywords: [chickens, backyard, eggs, pros and cons, bigger is better]
author-note:
  disclosures:
    conflict of interest: The authors have no conflicts of interest to declare.
  financial-support: "This study was supported by a grant from The International Society for Fowl Language."
  gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
impact-statement: "This study illustrates not only how, but also why one should raise big-ass backyard chickens. The results may be used by numerous individuals to convince their domestic partners (such as the second author's husband) to build a backyard coop and give in to the siren squawk of that sweet sweet chicken-raisin' lifestyle."
bibliography: Chickens.bib
format: 
  #apaquarto-docx: default 
  #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
  apaquarto-pdf: default
floatsintext: true
documentmode: man
donotrepeattitle: true
mainfont: "Times New Roman"
fontsize: 12pt

---

```{r, echo=FALSE, include=FALSE}

# Load necessary libraries
library(readr)
library(tidyverse)
library(ggplot2)
library(tidyverse)
library(flextable)

```

> *If you've ever seen a picture of Pechugas the Rooster (Fig. 1), your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct.*

![Pechugas the Rooster](Images_BigAssChicken/orpignton rooster.jpg){
  #fig-myimportedimage 
  width="4in" 
  fig-alt="A picture of Pechugas the Rooster being a Big-Ass Chicken." 
  apa-note="This is a Big-Ass Chicken."
  }

In recent decades, the practice of maintaining domestic poultry within urban and suburban residential settings has experienced a notable resurgence [@maceBackyardOurBeds2024]. This phenomenon, colloquially referred to as "backyard chicken keeping," represents a fascinating intersection of agricultural tradition and contemporary sustainability movements. The economic landscape has further accelerated this trend, as inflated egg prices have prompted an increasing number of households to consider domestic poultry as a pragmatic response to marketplace volatility [@italieSoaringEggPrices2025]. Indeed, consumer data suggests that the correlation between rising commercial egg costs and the purchase of chicken coops is remarkably robust[@kagayaPriceAttentionAnalysis2025].

[paragraph about why bigger is better, with regards to egg production and everything else]

Previous studies have largely focused either on large-scale commercial poultry operations or on historical agricultural practices [@bistSustainablePoultryFarming2024; @grzinicIntensivePoultryFarming2023; @jeniOverviewHealthChallenges2021].  While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution---a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate. Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the Big-Ass Chicken (BAC)[@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022]. This study aims to fill that obvious (and sizeable) gap.

# Current Study
Our research design employs a mixed methods approach to develop a nuanced understanding of this increasingly common practice. The methodology combines quantitative data analysis examining multiple factors related to Big-Ass backyard chicken husbandry---including analysis of factors related to chicken size and egg production---with qualitative thematic analysis of in-depth interviews conducted with chicken owners of BAC's. By triangulating these methodological approaches, we aspire to move beyond anecdotal evidence and develop an empirically robust understanding of what might be termed the "net hennefit" of backyard chicken husbandry in contemporary urban contexts. The present study thus investigates two hypotheses: 
1. The benefits of maintaining a small flock of Gallus gallus domesticus (see Figure 2) in residential settings significantly outweigh the associated challenges and drawbacks.
2. Raising BAC's will result in an increased number of perceived benefits relative to drawbacks.

![Gallus gallus domesticus](Images_BigAssChicken/Orpignton hen(edgar).jpg){
  #fig-orpington-chicken
  width="4in" 
  fig-alt="A picture of a common backyard chicken." 
  apa-note="Also known as the Orpington chicken."
  }

# Method
## Participants
### Chickens
We looked at 50 Gallus gallus domesticus chicks, starting from hatching...

### Humans
Semi-structured interviews were conducted with 50 urban backyard chicken keepers (32 female, 17 male, 1 non-binary) across three metropolitan areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15). Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = 3.7 years). Flock sizes ranged from 2-15 birds (median = 4).

## Procedure
### Quantitative
We measured the weight of chickens ....

### Qualitative
Semi-structured interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis. Initial coding was conducted independently by two researchers, followed by collaborative theme development. Member-checking was employed with a subset of 12 participants to verify thematic authenticity.

## Measures
### Quantitative

### Qualitative
thematic analysis

# Results
## Chickens  
```{r, echo=FALSE, include=FALSE}

#| label: data-analysis

## Reading the data 
chicken_weight = read.csv("Data_BigAssChicken/ChickWeight.csv")

# head(chicken_data)
## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
chicken_weight = as_tibble(chicken_weight)

chicken_weight = chicken_weight %>%
  select((-c(X)))

head(chicken_weight)

## Changing the 'weight' column name to 'Weight' so everything remains consistent in terms of capitalization
chicken_weight = chicken_weight %>%
  rename(Weight = weight)
```

```{r, echo=FALSE}
## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))

ggplot(chicken_weight, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()

```

```{r, echo=FALSE, include=FALSE}
## Ok now we have visualized the different growth trends of the various chickens. Now we probably want to look at how diet might factor into this trend. First let's calculate the mean growth rates of all the various chickens according to diet (rated 1 to 4)

## Basic mathematical premise: end - start / start gives us the growth rate for a single period. Then we just add all the individual growth rates and divide by the number of periods

chicken_weight = chicken_weight %>%
  arrange(Chick, Time) %>%
  group_by(Chick) %>%
  mutate(GrowRate = (Weight - first(Weight)) / (Time - first(Time))) %>%
  ungroup()

## Now analyzing with diets

dGrowRate = chicken_weight %>%
  group_by(Diet) %>%
  summarise(meanGrowRate = mean(GrowRate, na.rm = TRUE))

print(dGrowRate)
```

```{r, echo=FALSE}
## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.

ggplot(dGrowRate, aes(x = Diet, y = meanGrowRate, fill = Diet)) + geom_bar(stat = "identity") + labs(x = "Diet", y = "Mean Growth Rate", title = "Figure 2: Mean Growth Rate Bar Plot (rate per day)") + theme_minimal()

```

```{r, echo=FALSE, include=FALSE}
## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression. Let's try that now.

lmWeight = lm(Weight ~ Time + Diet, data = chicken_weight)
summary(lmWeight)

## So we see that both time and diet are significant predictors of weight. Meaning a one unit increase in time (which actually means going from 0 to 2, or 2 to 4, etc) corresponds with an 8.77 gram increase in weight. In addition, a one unit increase in diet (meaning going from diet 1 to 2, 2 to 3, or 3 to 4) corresponds with an 11.78 gram increase in weight. So the interpretation is that if using diet 4 as opposed to diet 1, you would see on average approximately a 33 gram weight increase.

```

```{r}
#| echo: FALSE
#| label: regression-plot
#| fig-cap: Regression of Weight on Time by Diet

## Finally, plotting the regression.
ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")

```

## Eggs

## Owners: Qualitative Themes and Subthemes 
Thematic Analysis of the transcribed interviews revealed five major themes: Economic Pragmatism, Self-Sufficiency and Food Security, Social and Community Dimensions, Practical Challenges and Adaptations, and Psychological and Emotional Benefits.

### 1. Economic Pragmatism

#### 1.1 Response to Market Volatility
Participants frequently cited economic considerations as initial motivations for chicken keeping, with 38 participants (76%) specifically mentioning rising egg prices:

> "When eggs hit seven dollars a dozen last winter, that was my tipping point. I did the math and realized a coop would pay for itself within a year." (Participant 23, Midwest)

> "My Jersey Giants [BACs] lay fewer eggs than production breeds, but each egg is nearly twice the size. One of my BAC eggs equals two store-bought large eggs in recipes, so the economics actually work out better for my family of five." (Participant 4, Eastern Seaboard, BAC owner)

#### 1.2 Beyond Simple Cost Calculations
While economic benefits served as initial motivations, participants described a more complex value proposition that extended beyond mere cost savings:

> "It's not just about saving money on eggs anymore. There's value in knowing exactly what my birds are eating, how they're treated, and connecting with my food source." (Participant 7, Eastern Seaboard)

#### 1.3 Unexpected Economic Benefits
Many participants (n=29, 58%) reported unanticipated economic advantages, including reduced food waste, garden fertilization, and pest control:

> "They eat all our kitchen scraps, turn them into eggs and fantastic compost. My garden has never been more productive, which means even more grocery savings." (Participant 42, Pacific Northwest)

### 2. Self-Sufficiency and Food Security

#### 2.1 Control Over Food Supply
A dominant theme emerged around increased feelings of food security and self-reliance:

> "After supply chain disruptions during COVID, having my own egg supply feels like insurance. No matter what happens at the grocery store, we've got breakfast." (Participant 11, Eastern Seaboard)

> "My Brahmas [BACs] aren't just egg layers—they're dual-purpose birds. In a true food security crisis, each bird represents about 10 pounds of meat. I don't plan to eat them, but there's peace of mind knowing these massive birds could feed my family for weeks if necessary." (Participant 29, Midwest, BAC owner)

#### 2.2 Quality and Freshness
Nearly all participants (n=47, 94%) emphasized superior egg quality as a significant benefit:

> "Store-bought eggs are a completely different food. Once you've had eggs with those vibrant orange yolks from your backyard, there's no comparison." (Participant 39, Pacific Northwest)

#### 2.3 Stepping Stone to Greater Self-Reliance
Many participants (n=31, 62%) described chicken keeping as part of a broader trajectory toward increased self-sufficiency:

> "The chickens were our gateway. Now we've got vegetable beds, rainwater collection, and we're thinking about beekeeping next year." (Participant 28, Midwest)

### 3. Social and Community Dimensions

#### 3.1 Neighborhood Connections
Unexpectedly, chicken keeping frequently facilitated community building:

> "Our chickens are neighborhood celebrities. Kids stop by after school, neighbors trade garden produce for eggs, and we've met people on our street we never spoke to before." (Participant 3, Eastern Seaboard)

> "My Cochin giants [BACs] are absolute neighborhood attractions. People literally schedule visits to see these fluffy behemoths. I've started hosting monthly 'Big-Ass Chicken Socials' where neighbors bring drinks and appetizers just to hang out with these gentle giants. They've become community mascots." (Participant 36, Pacific Northwest, BAC owner)

#### 3.2 Educational Value
Families with children (n=22) universally cited educational benefits:

> "My kids understand where food comes from. They've witnessed the whole life cycle, learned responsibility through daily care, and developed empathy for animals." (Participant 45, Pacific Northwest)

#### 3.3 Negotiating Regulations and Relationships
Navigating municipal regulations and neighbor relationships emerged as significant challenges:

> "Getting the permit was straightforward, but keeping peace with one particular neighbor has been ongoing diplomacy. Giving them free eggs helps." (Participant 19, Midwest)

### 4. Practical Challenges and Adaptations

#### 4.1 Time Commitment Reality
Time requirements emerged as the most frequently cited challenge (n=41, 82%):

> "The daily care is minimal, maybe 10 minutes. But when something goes wrong—a predator gets in, or a bird gets sick—suddenly it's very time-intensive." (Participant 34, Pacific Northwest)

> "Keeping BACs requires special planning. My Orpingtons eat nearly twice what standard birds consume, and their massive droppings mean more frequent coop cleaning. The flip side is that predators leave them completely alone—even neighborhood dogs keep their distance from these 12-pound behemoths. No raccoon is brave enough to take on my roosters." (Participant 12, Eastern Seaboard, BAC owner)

#### 4.2 Seasonal Variability
Participants described adapting to natural laying cycles:

> "Winter egg production drops dramatically. You either accept buying eggs for a few months or install coop lighting, which raises ethical questions about manipulating their natural cycles." (Participant 8, Eastern Seaboard)

#### 4.3 Learning Curve and Resource Networks
Most participants (n=43, 86%) described a significant learning curve, mitigated by online communities:

> "YouTube and Facebook groups were lifesavers. There's always someone online who's dealt with whatever weird chicken situation you're facing at 11 PM." (Participant 14, Midwest)

### 5. Psychological and Emotional Benefits

#### 5.1 Stress Reduction
An unexpected theme emerged around the stress-reducing properties of chicken keeping:

> "Watching the chickens scratch and peck is meditative. After a stressful workday, I'll sit with a cup of tea and just observe them. Better than therapy." (Participant 31, Midwest)

> "There's something profoundly calming about my Australorps [BACs]. Their size makes them move more slowly and deliberately than smaller breeds. My blood pressure literally drops when I'm with them. After my heart attack, my cardiologist actually wrote 'BAC therapy' into my recovery plan—jokingly, but I take it seriously. Spending time with these gentle giants is legitimately therapeutic." (Participant 25, Midwest, BAC owner)

#### 5.2 Connection to Agricultural Heritage
Many participants (n=26, 52%) described chicken keeping as connecting them to family heritage:

> "My grandmother kept chickens. When I collect eggs, I feel connected to her and generations of women in my family who did this same simple act." (Participant 5, Eastern Seaboard)

#### 5.3 Identity and Values Alignment
Chicken keeping frequently represented an expression of environmental and ethical values:

> "It's living my values around humane animal treatment, reducing my carbon footprint, and stepping outside the industrial food system, even if in a small way." (Participant 47, Pacific Northwest)

# Discussion
The findings of this study underscore the economic, environmental, and social benefits of backyard chicken keeping while also highlighting the practical challenges that accompany this practice. Our results provide empirical support for the growing movement toward urban and suburban poultry husbandry, illustrating how households recover their initial investments and experience broader benefits related to sustainability and well-being.

### Economic Considerations

One of the most compelling findings is the financial feasibility of backyard chicken keeping. Despite an initial setup cost averaging $487, most participants reported recouping their investments within 14 months through egg production and additional savings in food waste reduction and garden fertilization. This aligns with previous research on urban agriculture, which emphasizes self-sufficiency and cost savings as key motivators [@maceBackyardOurBeds2024]. Notably, owners of Big-Ass Chickens (BACs) described a cost-benefit ratio due to the larger egg sizes and increased meat yield potential.

The study also highlights how economic motivations evolve over time. While rising commercial egg prices may initially drive adoption, many owners ultimately find additional value in food security, ethical treatment of animals, and sustainability. These findings suggest that policymakers and sustainability advocates could leverage economic incentives to promote backyard chicken keeping as a viable food security measure, particularly in urban settings.

### Environmental and Sustainability Benefits

In addition to economic advantages, backyard chicken keeping contributes to environmental sustainability by reducing food waste and enhancing soil quality. Participants widely reported using chickens to process kitchen scraps, turning waste into high-quality compost that improved garden productivity. This finding complements existing literature on the role of urban agriculture in sustainable food systems [@grzinicIntensivePoultryFarming2023].

The contribution of this study is the exploration of BACs in sustainability efforts. Owners of larger breeds emphasized their birds' dual-purpose roles, noting their ability to provide both eggs and meat. Furthermore, their robust size and temperament reportedly made them more resistant to predation, reducing flock losses. Future research could examine how breed selection influences long-term sustainability outcomes in urban poultry keeping.

### Social and Psychological Benefits

Beyond economic and environmental factors, this study reveals the significant social and emotional benefits associated with backyard chicken keeping. Many participants reported stronger neighborhood connections facilitated by chicken ownership, with some even organizing community events centered around their flocks. This aligns with prior research on urban agriculture’s role in fostering social cohesion [@singhBackyardPoultryFarming2022]

Psychologically, many owners described their chickens as sources of emotional support, with several likening them to pets. Participants noted stress reduction, increased outdoor activity, and a sense of accomplishment in maintaining their flocks. These findings suggest that backyard chicken keeping may serve as a form of therapeutic engagement, particularly for individuals seeking greater interaction with nature.

###Practical Challenges and Considerations

Despite the numerous benefits, backyard chicken keeping is not without challenges. Time commitment emerged as a key issue, with participants spending an average of 28 minutes per day on maintenance tasks. While many found the routine manageable, unexpected events such as illness, predation, or extreme weather—could significantly increase time demands.

Navigating municipal regulations also posed a notable challenge. Many participants encountered restrictions on flock size, coop placement, and noise levels, requiring negotiation with local authorities and neighbors. These findings highlight the need for clear and accessible regulatory guidelines to support responsible backyard chicken keeping.

Seasonal variations in productivity were another important consideration. Egg production naturally fluctuates based on daylight hours and molting cycles, requiring owners to plan accordingly. Some participants mitigated these challenges by supplementing light exposure or adjusting flock composition to include breeds with higher winter laying rates.

## Conclusion

This  study supports the hypothesis that the benefits of backyard chicken keeping outweigh the challenges. However, success depends on household-specific variables, including available space, time commitment, and municipal regulations. The inclusion of BACs as a focal point of this study provides unique insights into breed selection and its implications for economic and sustainability outcomes.

Future research should further explore the long-term impacts of backyard chicken keeping on food security, community engagement, and mental health. Additionally, policymakers should consider strategies to facilitate responsible poultry keeping through supportive legislation and educational resources. By addressing these factors, backyard chicken keeping can continue to grow as a viable and sustainable practice in urban and suburban communities.

# References

### 2025-03-05 BAC_Manuscript_Final.tex
chages and organizing of repo

\documentclass[
  man,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

\usepackage{amsmath}
\usepackage{amssymb}

\RequirePackage{longtable}
\RequirePackage{threeparttablex}

\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-.5em}%
	{\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-\z@\relax}%
	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

\usepackage{tcolorbox}
\tcbuselibrary{listings,theorems, breakable, skins}
\usepackage{fontawesome5}

\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}

%\newlength\Oldarrayrulewidth
%\newlength\Oldtabcolsep

\usepackage{hyperref}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{fontspec}

\defaultfontfeatures{Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

  \setmainfont[,RawFeature={fallback=mainfontfallback}]{Times New Roman}

\title{That's a Big-Ass Chicken: A Mixed Methods Examination of Urban
Backyard Chicken Husbandry}

\shorttitle{That's a Big-Ass Chicken}

\usepackage{etoolbox}

\authorsnames{Karen Veronica Becerra,Kristen M. Johnson,Michael Moroz}

\affiliation{
{Department of Psychology, The University of Chicago}}

\leftheader{Becerra, Johnson and Moroz}

\abstract{This study investigates the growing phenomenon of backyard
chicken keeping in urban and suburban environments, a practice that has
gained significant momentum amid rising commercial egg prices. Employing
a mixed methods approach, we analyzed quantitative data from
\_\_\_\_\_\_. Concurrently, we conducted thematic analysis of in-depth
interviews with backyard chicken owners to explore perceived benefits
and challenges. Our findings indicate that while initial setup costs
average \$487, households recover this investment within 14 months
through egg production, with additional benefits including reduced food
waste, improved garden soil quality, and reported increases in household
well-being. Challenges identified include time commitment (averaging 28
minutes daily), navigating municipal regulations, and managing seasonal
variations in productivity. Factor analysis revealed that success
factors cluster around three dimensions: appropriate infrastructure,
consistent maintenance routines, and community support networks.
Ultimately, our results support the hypothesis that the benefits of
backyard chicken keeping outweigh the challenges for most practitioners,
though successful implementation depends on household-specific variables
and community context. This research contributes to growing literature
on urban agriculture while providing practical insights for potential
chicken keepers, municipal policymakers, and sustainability
advocates.  \section{} \noindent This study illustrates not only how,
but also why one should raise big-ass backyard chickens. The results may
be used by numerous individuals to convince their domestic partners
(such as the second author's husband) to build a backyard coop and give
in to the siren squawk of that sweet sweet chicken-raisin' lifestyle. }

\keywords{chickens, backyard, eggs, pros and cons, bigger is better}

\authornote{\par{\addORCIDlink{Karen Veronica
Becerra}{0009-0006-4967-0955}}\par{\addORCIDlink{Kristen M.
Johnson}{0009-0008-3757-5795}}\par{\addORCIDlink{Michael
Moroz}{0009-0000-9772-0001}}

\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Karen
Veronica Becerra:   conceptualization, formal
anlaysis, methodology, project
administration, software, visualization, editing; Kristen M.
Johnson:   conceptualization, data curation, methodology, project
administration, software, writing, editing; Michael Moroz:   formal
anlaysis, software, visualization, editing}
\par{Correspondence concerning this article should be addressed to Karen
Veronica Becerra, Department of Psychology, The University of
Chicago, 5848 S. University
Avenue, Chicago, IL 60637, USA, Email: kvbecerra@Uchicago.edu}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother

\urlstyle{same}

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

% From https://tex.stackexchange.com/a/645996/211326
%%% apa7 doesn't want to add appendix section titles in the toc
%%% let's make it do it
\makeatletter
\xpatchcmd{\appendix}
  {\par}
  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
  {}{}
\makeatother

%% Disable longtable counter
%% https://tex.stackexchange.com/a/248395/211326

\usepackage{etoolbox}

\makeatletter
\patchcmd{\LT@caption}
  {\bgroup}
  {\bgroup\global\LTpatch@captiontrue}
  {}{}
\patchcmd{\longtable}
  {\par}
  {\par\global\LTpatch@captionfalse}
  {}{}
\apptocmd{\endlongtable}
  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
  {}{}
\newif\ifLTpatch@caption
\makeatother

\begin{document}

\maketitle

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setlength\LTleft{0pt}

\begin{quote}
\emph{If you've ever seen a picture of Pechugas the Rooster (Fig. 1),
your first words would invariably be ``That's a Big-Ass Chicken!'' And
you would be correct.}
\end{quote}

\begin{figure}[!htbp]

{\caption{{Pechugas the Rooster}{\label{fig-myimportedimage}}}}

\includegraphics[width=4in,height=\textheight,keepaspectratio]{Images_BigAssChicken/orpignton rooster.jpg}

{\noindent \emph{Note.} This is a Big-Ass Chicken.}

\end{figure}

In recent decades, the practice of maintaining domestic poultry within
urban and suburban residential settings has experienced a notable
resurgence (\citeproc{ref-maceBackyardOurBeds2024}{Mace \& Knight,
2024}). This phenomenon, colloquially referred to as ``backyard chicken
keeping,'' represents a fascinating intersection of agricultural
tradition and contemporary sustainability movements. The economic
landscape has further accelerated this trend, as inflated egg prices
have prompted an increasing number of households to consider domestic
poultry as a pragmatic response to marketplace volatility
(\citeproc{ref-italieSoaringEggPrices2025}{Italie, 2025}). Indeed,
consumer data suggests that the correlation between rising commercial
egg costs and the purchase of chicken coops is remarkably
robust(\citeproc{ref-kagayaPriceAttentionAnalysis2025}{Kagaya et al.,
2025}).

{[}paragraph about why bigger is better, with regards to egg production
and everything else{]}

Previous studies have largely focused either on large-scale commercial
poultry operations or on historical agricultural practices
(\citeproc{ref-bistSustainablePoultryFarming2024}{Bist et al., 2024};
\citeproc{ref-grzinicIntensivePoultryFarming2023}{Gržinić et al., 2023};
\citeproc{ref-jeniOverviewHealthChallenges2021}{Jeni et al., 2021}).
While proponents extol the virtues of fresh eggs and animated garden
assistants, detractors cite concerns ranging from zoonotic disease
transmission to neighborhood noise pollution---a concern that anyone who
has experienced a rooster's enthusiasm for announcing dawn can readily
appreciate. Surprisingly, of those studies that do consider the costs
and benefits of backyard chicken keeping, none that to the authors
knowledge look into the phenomenon of the Big-Ass Chicken
(BAC)(\citeproc{ref-ayalaReviewPathogenTransmission2020}{Ayala et al.,
2020}; \citeproc{ref-fischerDefenceBackyardChickens2019}{Fischer \&
Milburn, 2019};
\citeproc{ref-schindlerBackyardChickensFrontYard}{Schindler, n.d.};
\citeproc{ref-singhBackyardPoultryFarming2022}{Singh et al., 2022}).
This study aims to fill that obvious (and sizeable) gap.

\section{Current Study}\label{current-study}

Our research design employs a mixed methods approach to develop a
nuanced understanding of this increasingly common practice. The
methodology combines quantitative data analysis examining multiple
factors related to Big-Ass backyard chicken husbandry---including
analysis of factors related to chicken size and egg production---with
qualitative thematic analysis of in-depth interviews conducted with
chicken owners of BAC's. By triangulating these methodological
approaches, we aspire to move beyond anecdotal evidence and develop an
empirically robust understanding of what might be termed the ``net
hennefit'' of backyard chicken husbandry in contemporary urban contexts.
The present study thus investigates two hypotheses: 1. The benefits of
maintaining a small flock of Gallus gallus domesticus (see Figure 2) in
residential settings significantly outweigh the associated challenges
and drawbacks. 2. Raising BAC's will result in an increased number of
perceived benefits relative to drawbacks.

\begin{figure}[!htbp]

{\caption{{Gallus gallus domesticus}{\label{fig-orpington-chicken}}}}

\includegraphics[width=4in,height=\textheight,keepaspectratio]{Images_BigAssChicken/Orpignton hen(edgar).jpg}

{\noindent \emph{Note.} Also known as the Orpington chicken.}

\end{figure}

\section{Method}\label{method}

\subsection{Participants}\label{participants}

\subsubsection{Chickens}\label{chickens}

We looked at 50 Gallus gallus domesticus chicks, starting from
hatching\ldots{}

\subsubsection{Humans}\label{humans}

Semi-structured interviews were conducted with 50 urban backyard chicken
keepers (32 female, 17 male, 1 non-binary) across three metropolitan
areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15).
Participants had maintained backyard chickens for periods ranging from 6
months to 12 years (mean = 3.7 years). Flock sizes ranged from 2-15
birds (median = 4).

\subsection{Procedure}\label{procedure}

\subsubsection{Quantitative}\label{quantitative}

We measured the weight of chickens \ldots.

\subsubsection{Qualitative}\label{qualitative}

Semi-structured interviews lasting 45-90 minutes were audio-recorded,
transcribed verbatim, and analyzed using Braun and Clarke's (2006)
six-phase approach to thematic analysis. Initial coding was conducted
independently by two researchers, followed by collaborative theme
development. Member-checking was employed with a subset of 12
participants to verify thematic authenticity.

\subsection{Measures}\label{measures}

\subsubsection{Quantitative}\label{quantitative-1}

\subsubsection{Qualitative}\label{qualitative-1}

thematic analysis

\section{Results}\label{results}

\subsection{Chickens}\label{chickens-1}

\pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/unnamed-chunk-3-1.pdf}}

\pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/unnamed-chunk-5-1.pdf}}

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

\begin{figure}[H]

\caption{Regression of Weight on Time by Diet}

{\centering \pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/regression-plot-1.pdf}}

}

\end{figure}%

\subsection{Eggs}\label{eggs}

\subsection{Owners: Qualitative Themes and
Subthemes}\label{owners-qualitative-themes-and-subthemes}

Thematic Analysis of the transcribed interviews revealed five major
themes: Economic Pragmatism, Self-Sufficiency and Food Security, Social
and Community Dimensions, Practical Challenges and Adaptations, and
Psychological and Emotional Benefits.

\subsubsection{1. Economic Pragmatism}\label{economic-pragmatism}

\paragraph{1.1 Response to Market
Volatility.}\label{response-to-market-volatility}

Participants frequently cited economic considerations as initial
motivations for chicken keeping, with 38 participants (76\%)
specifically mentioning rising egg prices:

\begin{quote}
``When eggs hit seven dollars a dozen last winter, that was my tipping
point. I did the math and realized a coop would pay for itself within a
year.'' (Participant 23, Midwest)
\end{quote}

\begin{quote}
``My Jersey Giants {[}BACs{]} lay fewer eggs than production breeds, but
each egg is nearly twice the size. One of my BAC eggs equals two
store-bought large eggs in recipes, so the economics actually work out
better for my family of five.'' (Participant 4, Eastern Seaboard, BAC
owner)
\end{quote}

\paragraph{1.2 Beyond Simple Cost
Calculations.}\label{beyond-simple-cost-calculations}

While economic benefits served as initial motivations, participants
described a more complex value proposition that extended beyond mere
cost savings:

\begin{quote}
``It's not just about saving money on eggs anymore. There's value in
knowing exactly what my birds are eating, how they're treated, and
connecting with my food source.'' (Participant 7, Eastern Seaboard)
\end{quote}

\paragraph{1.3 Unexpected Economic
Benefits.}\label{unexpected-economic-benefits}

Many participants (n=29, 58\%) reported unanticipated economic
advantages, including reduced food waste, garden fertilization, and pest
control:

\begin{quote}
``They eat all our kitchen scraps, turn them into eggs and fantastic
compost. My garden has never been more productive, which means even more
grocery savings.'' (Participant 42, Pacific Northwest)
\end{quote}

\subsubsection{2. Self-Sufficiency and Food
Security}\label{self-sufficiency-and-food-security}

\paragraph{2.1 Control Over Food
Supply.}\label{control-over-food-supply}

A dominant theme emerged around increased feelings of food security and
self-reliance:

\begin{quote}
``After supply chain disruptions during COVID, having my own egg supply
feels like insurance. No matter what happens at the grocery store, we've
got breakfast.'' (Participant 11, Eastern Seaboard)
\end{quote}

\begin{quote}
``My Brahmas {[}BACs{]} aren't just egg layers---they're dual-purpose
birds. In a true food security crisis, each bird represents about 10
pounds of meat. I don't plan to eat them, but there's peace of mind
knowing these massive birds could feed my family for weeks if
necessary.'' (Participant 29, Midwest, BAC owner)
\end{quote}

\paragraph{2.2 Quality and Freshness.}\label{quality-and-freshness}

Nearly all participants (n=47, 94\%) emphasized superior egg quality as
a significant benefit:

\begin{quote}
``Store-bought eggs are a completely different food. Once you've had
eggs with those vibrant orange yolks from your backyard, there's no
comparison.'' (Participant 39, Pacific Northwest)
\end{quote}

\paragraph{2.3 Stepping Stone to Greater
Self-Reliance.}\label{stepping-stone-to-greater-self-reliance}

Many participants (n=31, 62\%) described chicken keeping as part of a
broader trajectory toward increased self-sufficiency:

\begin{quote}
``The chickens were our gateway. Now we've got vegetable beds, rainwater
collection, and we're thinking about beekeeping next year.''
(Participant 28, Midwest)
\end{quote}

\subsubsection{3. Social and Community
Dimensions}\label{social-and-community-dimensions}

\paragraph{3.1 Neighborhood
Connections.}\label{neighborhood-connections}

Unexpectedly, chicken keeping frequently facilitated community building:

\begin{quote}
``Our chickens are neighborhood celebrities. Kids stop by after school,
neighbors trade garden produce for eggs, and we've met people on our
street we never spoke to before.'' (Participant 3, Eastern Seaboard)
\end{quote}

\begin{quote}
``My Cochin giants {[}BACs{]} are absolute neighborhood attractions.
People literally schedule visits to see these fluffy behemoths. I've
started hosting monthly `Big-Ass Chicken Socials' where neighbors bring
drinks and appetizers just to hang out with these gentle giants. They've
become community mascots.'' (Participant 36, Pacific Northwest, BAC
owner)
\end{quote}

\paragraph{3.2 Educational Value.}\label{educational-value}

Families with children (n=22) universally cited educational benefits:

\begin{quote}
``My kids understand where food comes from. They've witnessed the whole
life cycle, learned responsibility through daily care, and developed
empathy for animals.'' (Participant 45, Pacific Northwest)
\end{quote}

\paragraph{3.3 Negotiating Regulations and
Relationships.}\label{negotiating-regulations-and-relationships}

Navigating municipal regulations and neighbor relationships emerged as
significant challenges:

\begin{quote}
``Getting the permit was straightforward, but keeping peace with one
particular neighbor has been ongoing diplomacy. Giving them free eggs
helps.'' (Participant 19, Midwest)
\end{quote}

\subsubsection{4. Practical Challenges and
Adaptations}\label{practical-challenges-and-adaptations}

\paragraph{4.1 Time Commitment Reality.}\label{time-commitment-reality}

Time requirements emerged as the most frequently cited challenge (n=41,
82\%):

\begin{quote}
``The daily care is minimal, maybe 10 minutes. But when something goes
wrong---a predator gets in, or a bird gets sick---suddenly it's very
time-intensive.'' (Participant 34, Pacific Northwest)
\end{quote}

\begin{quote}
``Keeping BACs requires special planning. My Orpingtons eat nearly twice
what standard birds consume, and their massive droppings mean more
frequent coop cleaning. The flip side is that predators leave them
completely alone---even neighborhood dogs keep their distance from these
12-pound behemoths. No raccoon is brave enough to take on my roosters.''
(Participant 12, Eastern Seaboard, BAC owner)
\end{quote}

\paragraph{4.2 Seasonal Variability.}\label{seasonal-variability}

Participants described adapting to natural laying cycles:

\begin{quote}
``Winter egg production drops dramatically. You either accept buying
eggs for a few months or install coop lighting, which raises ethical
questions about manipulating their natural cycles.'' (Participant 8,
Eastern Seaboard)
\end{quote}

\paragraph{4.3 Learning Curve and Resource
Networks.}\label{learning-curve-and-resource-networks}

Most participants (n=43, 86\%) described a significant learning curve,
mitigated by online communities:

\begin{quote}
``YouTube and Facebook groups were lifesavers. There's always someone
online who's dealt with whatever weird chicken situation you're facing
at 11 PM.'' (Participant 14, Midwest)
\end{quote}

\subsubsection{5. Psychological and Emotional
Benefits}\label{psychological-and-emotional-benefits}

\paragraph{5.1 Stress Reduction.}\label{stress-reduction}

An unexpected theme emerged around the stress-reducing properties of
chicken keeping:

\begin{quote}
``Watching the chickens scratch and peck is meditative. After a
stressful workday, I'll sit with a cup of tea and just observe them.
Better than therapy.'' (Participant 31, Midwest)
\end{quote}

\begin{quote}
``There's something profoundly calming about my Australorps {[}BACs{]}.
Their size makes them move more slowly and deliberately than smaller
breeds. My blood pressure literally drops when I'm with them. After my
heart attack, my cardiologist actually wrote `BAC therapy' into my
recovery plan---jokingly, but I take it seriously. Spending time with
these gentle giants is legitimately therapeutic.'' (Participant 25,
Midwest, BAC owner)
\end{quote}

\paragraph{5.2 Connection to Agricultural
Heritage.}\label{connection-to-agricultural-heritage}

Many participants (n=26, 52\%) described chicken keeping as connecting
them to family heritage:

\begin{quote}
``My grandmother kept chickens. When I collect eggs, I feel connected to
her and generations of women in my family who did this same simple
act.'' (Participant 5, Eastern Seaboard)
\end{quote}

\paragraph{5.3 Identity and Values
Alignment.}\label{identity-and-values-alignment}

Chicken keeping frequently represented an expression of environmental
and ethical values:

\begin{quote}
``It's living my values around humane animal treatment, reducing my
carbon footprint, and stepping outside the industrial food system, even
if in a small way.'' (Participant 47, Pacific Northwest)
\end{quote}

\section{Discussion}\label{discussion}

The findings of this study underscore the economic, environmental, and
social benefits of backyard chicken keeping while also highlighting the
practical challenges that accompany this practice. Our results provide
empirical support for the growing movement toward urban and suburban
poultry husbandry, illustrating how households recover their initial
investments and experience broader benefits related to sustainability
and well-being.

\subsubsection{Economic Considerations}\label{economic-considerations}

One of the most compelling findings is the financial feasibility of
backyard chicken keeping. Despite an initial setup cost averaging \$487,
most participants reported recouping their investments within 14 months
through egg production and additional savings in food waste reduction
and garden fertilization. This aligns with previous research on urban
agriculture, which emphasizes self-sufficiency and cost savings as key
motivators (\citeproc{ref-maceBackyardOurBeds2024}{Mace \& Knight,
2024}). Notably, owners of Big-Ass Chickens (BACs) described a
cost-benefit ratio due to the larger egg sizes and increased meat yield
potential.

The study also highlights how economic motivations evolve over time.
While rising commercial egg prices may initially drive adoption, many
owners ultimately find additional value in food security, ethical
treatment of animals, and sustainability. These findings suggest that
policymakers and sustainability advocates could leverage economic
incentives to promote backyard chicken keeping as a viable food security
measure, particularly in urban settings.

\subsubsection{Environmental and Sustainability
Benefits}\label{environmental-and-sustainability-benefits}

In addition to economic advantages, backyard chicken keeping contributes
to environmental sustainability by reducing food waste and enhancing
soil quality. Participants widely reported using chickens to process
kitchen scraps, turning waste into high-quality compost that improved
garden productivity. This finding complements existing literature on the
role of urban agriculture in sustainable food systems
(\citeproc{ref-grzinicIntensivePoultryFarming2023}{Gržinić et al.,
2023}).

The contribution of this study is the exploration of BACs in
sustainability efforts. Owners of larger breeds emphasized their birds'
dual-purpose roles, noting their ability to provide both eggs and meat.
Furthermore, their robust size and temperament reportedly made them more
resistant to predation, reducing flock losses. Future research could
examine how breed selection influences long-term sustainability outcomes
in urban poultry keeping.

\subsubsection{Social and Psychological
Benefits}\label{social-and-psychological-benefits}

Beyond economic and environmental factors, this study reveals the
significant social and emotional benefits associated with backyard
chicken keeping. Many participants reported stronger neighborhood
connections facilitated by chicken ownership, with some even organizing
community events centered around their flocks. This aligns with prior
research on urban agriculture's role in fostering social cohesion
(\citeproc{ref-singhBackyardPoultryFarming2022}{Singh et al., 2022})

Psychologically, many owners described their chickens as sources of
emotional support, with several likening them to pets. Participants
noted stress reduction, increased outdoor activity, and a sense of
accomplishment in maintaining their flocks. These findings suggest that
backyard chicken keeping may serve as a form of therapeutic engagement,
particularly for individuals seeking greater interaction with nature.

\#\#\#Practical Challenges and Considerations

Despite the numerous benefits, backyard chicken keeping is not without
challenges. Time commitment emerged as a key issue, with participants
spending an average of 28 minutes per day on maintenance tasks. While
many found the routine manageable, unexpected events such as illness,
predation, or extreme weather---could significantly increase time
demands.

Navigating municipal regulations also posed a notable challenge. Many
participants encountered restrictions on flock size, coop placement, and
noise levels, requiring negotiation with local authorities and
neighbors. These findings highlight the need for clear and accessible
regulatory guidelines to support responsible backyard chicken keeping.

Seasonal variations in productivity were another important
consideration. Egg production naturally fluctuates based on daylight
hours and molting cycles, requiring owners to plan accordingly. Some
participants mitigated these challenges by supplementing light exposure
or adjusting flock composition to include breeds with higher winter
laying rates.

\subsection{Conclusion}\label{conclusion}

This study supports the hypothesis that the benefits of backyard chicken
keeping outweigh the challenges. However, success depends on
household-specific variables, including available space, time
commitment, and municipal regulations. The inclusion of BACs as a focal
point of this study provides unique insights into breed selection and
its implications for economic and sustainability outcomes.

Future research should further explore the long-term impacts of backyard
chicken keeping on food security, community engagement, and mental
health. Additionally, policymakers should consider strategies to
facilitate responsible poultry keeping through supportive legislation
and educational resources. By addressing these factors, backyard chicken
keeping can continue to grow as a viable and sustainable practice in
urban and suburban communities.

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-ayalaReviewPathogenTransmission2020}
Ayala, A. J., Yabsley, M. J., \& Hernandez, S. M. (2020). A {Review} of
{Pathogen Transmission} at the {Backyard Chicken}--{Wild Bird
Interface}. \emph{Frontiers in Veterinary Science}, \emph{7}, 539925.
\url{https://doi.org/10.3389/fvets.2020.539925}

\bibitem[\citeproctext]{ref-bistSustainablePoultryFarming2024}
Bist, R. B., Bist, K., Poudel, S., Subedi, D., Yang, X., Paneru, B.,
Mani, S., Wang, D., \& Chai, L. (2024). Sustainable poultry farming
practices: A critical review of current strategies and future prospects.
\emph{Poultry Science}, \emph{103}(12), 104295.
\url{https://doi.org/10.1016/j.psj.2024.104295}

\bibitem[\citeproctext]{ref-fischerDefenceBackyardChickens2019}
Fischer, B., \& Milburn, J. (2019). In {Defence} of {Backyard Chickens}.
\emph{Journal of Applied Philosophy}, \emph{36}(1), 108--123.
\url{https://doi.org/10.1111/japp.12291}

\bibitem[\citeproctext]{ref-grzinicIntensivePoultryFarming2023}
Gržinić, G., Piotrowicz-Cieślak, A., Klimkowicz-Pawlas, A., Górny, R.
L., Ławniczek-Wałczyk, A., Piechowicz, L., Olkowska, E., Potrykus, M.,
Tankiewicz, M., Krupka, M., Siebielec, G., \& Wolska, L. (2023).
Intensive poultry farming: {A} review of the impact on the environment
and human health. \emph{Science of The Total Environment}, \emph{858},
160014. \url{https://doi.org/10.1016/j.scitotenv.2022.160014}

\bibitem[\citeproctext]{ref-italieSoaringEggPrices2025}
Italie, L. (2025). Soaring egg prices have more people looking into
backyard chickens {\textbar} {AP News}. \emph{AP News}.

\bibitem[\citeproctext]{ref-jeniOverviewHealthChallenges2021}
Jeni, R. E., Dittoe, D. K., Olson, E. G., Lourenco, J., Seidel, D. S.,
Ricke, S. C., \& Callaway, T. R. (2021). An overview of health
challenges in alternative poultry production systems. \emph{Poultry
Science}, \emph{100}(7), 101173.
\url{https://doi.org/10.1016/j.psj.2021.101173}

\bibitem[\citeproctext]{ref-kagayaPriceAttentionAnalysis2025}
Kagaya, S., Widmar, N. O., \& Kilders, V. (2025). The price of
attention: {An} analysis of the intersection of media coverage and
public sentiments about eggs and egg prices. \emph{Poultry Science},
\emph{104}(1), 104482. \url{https://doi.org/10.1016/j.psj.2024.104482}

\bibitem[\citeproctext]{ref-maceBackyardOurBeds2024}
Mace, J. L., \& Knight, A. (2024). From the {Backyard} to {Our Beds}:
{The Spectrum} of {Care}, {Attitudes}, {Relationship Types}, and
{Welfare} in {Non-Commercial Chicken Care}. \emph{Animals},
\emph{14}(2), 288. \url{https://doi.org/10.3390/ani14020288}

\bibitem[\citeproctext]{ref-schindlerBackyardChickensFrontYard}
Schindler, S. B. (n.d.). \emph{Of {Backyard Chickens} and {FrontYard
Gardens}: {The Conflict Between Local Governments} and {Locavores}}.

\bibitem[\citeproctext]{ref-singhBackyardPoultryFarming2022}
Singh, M., Mollier, R. T., Paton, R. N., Pongener, N., Yadav, R., Singh,
V., Katiyar, R., Kumar, R., Sonia, C., Bhatt, M., Babu, S., Rajkhowa, D.
J., \& Mishra, V. K. (2022). Backyard poultry farming with improved
germplasm: {Sustainable} food production and nutritional security in
fragile ecosystem. \emph{Frontiers in Sustainable Food Systems},
\emph{6}, 962268. \url{https://doi.org/10.3389/fsufs.2022.962268}

\end{CSLReferences}

\end{document}

### 2025-03-06 BAC_Manuscript_Final.tex
changes

@@
 
+\begin{verbatim}
+#| label: data_analysis_2
+Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
+head(Egg_Size)
+\end{verbatim}
+
+\begin{verbatim}
+# Step 1: Install and load the dplyr package (if not installed)
+# install.packages("dplyr") # this if you haven't installed dplyr
+library(dplyr)
+
+# Step 2: Load the data
+Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
+
+# Step 3: Select relevant columns
+Egg_Size <- Egg_Size[, c("GallusBreed", "GallusEggWeight", "GallusWeight")]
+
+# Step 4: Remove rows with missing values
+Egg_Size <- na.omit(Egg_Size)
+
+# Step 5: Arrange the data by EggWeight in ascending order
+Egg_Size <- Egg_Size %>%
+  arrange(GallusEggWeight)
+
+# Step 6: Save the cleaned and sorted data to a new CSV file
+write.csv(Egg_Size, "Egg_Size_Data.csv", row.names = FALSE)
+
+# Step 7: View the cleaned and sorted data
+head(Egg_Size)
+\end{verbatim}
+
 \subsection{Owners: Qualitative Themes and

### 2025-03-06 Data_BigAssChicken/egg analysis .Rmd
changes

--- 2025-03-06 BAC_Manuscript_Final.tex
@@
-\documentclass[
-  man,
-  floatsintext,
-  longtable,
-  nolmodern,
-  notxfonts,
-  notimes,
-  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}
+---
+title: "egg analysis "
+output: html_document
+---
 
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\RequirePackage{longtable}
-\RequirePackage{threeparttablex}
-
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-	{-.5em}%
-	{\normalfont\normalsize\bfseries\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
-	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-	{-\z@\relax}%
-	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
-\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
-\setcounter{topnumber}{2}
-\setcounter{bottomnumber}{2}
-\setcounter{totalnumber}{4}
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\bottomfraction}{0.85}
-\renewcommand{\textfraction}{0.15}
-\renewcommand{\floatpagefraction}{0.7}
-
-\usepackage{tcolorbox}
-\tcbuselibrary{listings,theorems, breakable, skins}
-\usepackage{fontawesome5}
-
-\definecolor{quarto-callout-color}{HTML}{909090}
-\definecolor{quarto-callout-note-color}{HTML}{0758E5}
-\definecolor{quarto-callout-important-color}{HTML}{CC1914}
-\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
-\definecolor{quarto-callout-tip-color}{HTML}{00A047}
-\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
-\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
-\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
-\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
-\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
-\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
-\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}
-
-%\newlength\Oldarrayrulewidth
-%\newlength\Oldtabcolsep
-
-\usepackage{hyperref}
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-
-\usepackage{graphicx}
-\makeatletter
-\newsavebox\pandoc@box
-\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
-  \sbox\pandoc@box{#1}%
-  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
-  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
-  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
-  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
-  \else\usebox{\pandoc@box}%
-  \fi%
-}
-% Set default figure placement to htbp
-\def\fps@figure{htbp}
-\makeatother
-
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{fontspec}
-
-\defaultfontfeatures{Scale=MatchLowercase}
-\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-
-  \setmainfont[,RawFeature={fallback=mainfontfallback}]{Times New Roman}
-
-\title{That's a Big-Ass Chicken: A Mixed Methods Examination of Urban
-Backyard Chicken Husbandry}
-
-\shorttitle{That's a Big-Ass Chicken}
-
-\usepackage{etoolbox}
-
-\authorsnames{Karen Veronica Becerra,Kristen M. Johnson,Michael Moroz}
-
-\affiliation{
-{Department of Psychology, The University of Chicago}}
-
-\leftheader{Becerra, Johnson and Moroz}
-
-\abstract{This study investigates the growing phenomenon of backyard
-chicken keeping in urban and suburban environments, a practice that has
-gained significant momentum amid rising commercial egg prices. Employing
-a mixed methods approach, we analyzed quantitative data from
-\_\_\_\_\_\_. Concurrently, we conducted thematic analysis of in-depth
-interviews with backyard chicken owners to explore perceived benefits
-and challenges. Our findings indicate that while initial setup costs
-average \$487, households recover this investment within 14 months
-through egg production, with additional benefits including reduced food
-waste, improved garden soil quality, and reported increases in household
-well-being. Challenges identified include time commitment (averaging 28
-minutes daily), navigating municipal regulations, and managing seasonal
-variations in productivity. Factor analysis revealed that success
-factors cluster around three dimensions: appropriate infrastructure,
-consistent maintenance routines, and community support networks.
-Ultimately, our results support the hypothesis that the benefits of
-backyard chicken keeping outweigh the challenges for most practitioners,
-though successful implementation depends on household-specific variables
-and community context. This research contributes to growing literature
-on urban agriculture while providing practical insights for potential
-chicken keepers, municipal policymakers, and sustainability
-advocates.  \section{} \noindent This study illustrates not only how,
-but also why one should raise big-ass backyard chickens. The results may
-be used by numerous individuals to convince their domestic partners
-(such as the second author's husband) to build a backyard coop and give
-in to the siren squawk of that sweet sweet chicken-raisin' lifestyle. }
-
-\keywords{chickens, backyard, eggs, pros and cons, bigger is better}
-
-\authornote{\par{\addORCIDlink{Karen Veronica
-Becerra}{0009-0006-4967-0955}}\par{\addORCIDlink{Kristen M.
-Johnson}{0009-0008-3757-5795}}\par{\addORCIDlink{Michael
-Moroz}{0009-0000-9772-0001}}
-
-\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Karen
-Veronica Becerra:   conceptualization, formal
-anlaysis, methodology, project
-administration, software, visualization, editing; Kristen M.
-Johnson:   conceptualization, data curation, methodology, project
-administration, software, writing, editing; Michael Moroz:   formal
-anlaysis, software, visualization, editing}
-\par{Correspondence concerning this article should be addressed to Karen
-Veronica Becerra, Department of Psychology, The University of
-Chicago, 5848 S. University
-Avenue, Chicago, IL 60637, USA, Email: kvbecerra@Uchicago.edu}
-}
-
-\makeatletter
-\let\endoldlt\endlongtable
-\def\endlongtable{
-\hline
-\endoldlt
-}
-\makeatother
-
-\urlstyle{same}
-
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-
-% From https://tex.stackexchange.com/a/645996/211326
-%%% apa7 doesn't want to add appendix section titles in the toc
-%%% let's make it do it
-\makeatletter
-\xpatchcmd{\appendix}
-  {\par}
-  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
-  {}{}
-\makeatother
-
-%% Disable longtable counter
-%% https://tex.stackexchange.com/a/248395/211326
-
-\usepackage{etoolbox}
-
-\makeatletter
-\patchcmd{\LT@caption}
-  {\bgroup}
-  {\bgroup\global\LTpatch@captiontrue}
-  {}{}
-\patchcmd{\longtable}
-  {\par}
-  {\par\global\LTpatch@captionfalse}
-  {}{}
-\apptocmd{\endlongtable}
-  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
-  {}{}
-\newif\ifLTpatch@caption
-\makeatother
-
-\begin{document}
-
-\maketitle
-
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-
-\setlength\LTleft{0pt}
-
-\begin{quote}
-\emph{If you've ever seen a picture of Pechugas the Rooster (Fig. 1),
-your first words would invariably be ``That's a Big-Ass Chicken!'' And
-you would be correct.}
-\end{quote}
-
-\begin{figure}[!htbp]
-
-{\caption{{Pechugas the Rooster}{\label{fig-myimportedimage}}}}
-
-\includegraphics[width=4in,height=\textheight,keepaspectratio]{Images_BigAssChicken/orpignton rooster.jpg}
-
-{\noindent \emph{Note.} This is a Big-Ass Chicken.}
-
-\end{figure}
-
-In recent decades, the practice of maintaining domestic poultry within
-urban and suburban residential settings has experienced a notable
-resurgence (\citeproc{ref-maceBackyardOurBeds2024}{Mace \& Knight,
-2024}). This phenomenon, colloquially referred to as ``backyard chicken
-keeping,'' represents a fascinating intersection of agricultural
-tradition and contemporary sustainability movements. The economic
-landscape has further accelerated this trend, as inflated egg prices
-have prompted an increasing number of households to consider domestic
-poultry as a pragmatic response to marketplace volatility
-(\citeproc{ref-italieSoaringEggPrices2025}{Italie, 2025}). Indeed,
-consumer data suggests that the correlation between rising commercial
-egg costs and the purchase of chicken coops is remarkably
-robust(\citeproc{ref-kagayaPriceAttentionAnalysis2025}{Kagaya et al.,
-2025}).
-
-{[}paragraph about why bigger is better, with regards to egg production
-and everything else{]}
-
-Previous studies have largely focused either on large-scale commercial
-poultry operations or on historical agricultural practices
-(\citeproc{ref-bistSustainablePoultryFarming2024}{Bist et al., 2024};
-\citeproc{ref-grzinicIntensivePoultryFarming2023}{Gržinić et al., 2023};
-\citeproc{ref-jeniOverviewHealthChallenges2021}{Jeni et al., 2021}).
-While proponents extol the virtues of fresh eggs and animated garden
-assistants, detractors cite concerns ranging from zoonotic disease
-transmission to neighborhood noise pollution---a concern that anyone who
-has experienced a rooster's enthusiasm for announcing dawn can readily
-appreciate. Surprisingly, of those studies that do consider the costs
-and benefits of backyard chicken keeping, none that to the authors
-knowledge look into the phenomenon of the Big-Ass Chicken
-(BAC)(\citeproc{ref-ayalaReviewPathogenTransmission2020}{Ayala et al.,
-2020}; \citeproc{ref-fischerDefenceBackyardChickens2019}{Fischer \&
-Milburn, 2019};
-\citeproc{ref-schindlerBackyardChickensFrontYard}{Schindler, n.d.};
-\citeproc{ref-singhBackyardPoultryFarming2022}{Singh et al., 2022}).
-This study aims to fill that obvious (and sizeable) gap.
-
-\section{Current Study}\label{current-study}
-
-Our research design employs a mixed methods approach to develop a
-nuanced understanding of this increasingly common practice. The
-methodology combines quantitative data analysis examining multiple
-factors related to Big-Ass backyard chicken husbandry---including
-analysis of factors related to chicken size and egg production---with
-qualitative thematic analysis of in-depth interviews conducted with
-chicken owners of BAC's. By triangulating these methodological
-approaches, we aspire to move beyond anecdotal evidence and develop an
-empirically robust understanding of what might be termed the ``net
-hennefit'' of backyard chicken husbandry in contemporary urban contexts.
-The present study thus investigates two hypotheses: 1. The benefits of
-maintaining a small flock of Gallus gallus domesticus (see Figure 2) in
-residential settings significantly outweigh the associated challenges
-and drawbacks. 2. Raising BAC's will result in an increased number of
-perceived benefits relative to drawbacks.
-
-\begin{figure}[!htbp]
-
-{\caption{{Gallus gallus domesticus}{\label{fig-orpington-chicken}}}}
-
-\includegraphics[width=4in,height=\textheight,keepaspectratio]{Images_BigAssChicken/Orpignton hen(edgar).jpg}
-
-{\noindent \emph{Note.} Also known as the Orpington chicken.}
-
-\end{figure}
-
-\section{Method}\label{method}
-
-\subsection{Participants}\label{participants}
-
-\subsubsection{Chickens}\label{chickens}
-
-We looked at 50 Gallus gallus domesticus chicks, starting from
-hatching\ldots{}
-
-\subsubsection{Humans}\label{humans}
-
-Semi-structured interviews were conducted with 50 urban backyard chicken
-keepers (32 female, 17 male, 1 non-binary) across three metropolitan
-areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15).
-Participants had maintained backyard chickens for periods ranging from 6
-months to 12 years (mean = 3.7 years). Flock sizes ranged from 2-15
-birds (median = 4).
-
-\subsection{Procedure}\label{procedure}
-
-\subsubsection{Quantitative}\label{quantitative}
-
-We measured the weight of chickens \ldots.
-
-\subsubsection{Qualitative}\label{qualitative}
-
-Semi-structured interviews lasting 45-90 minutes were audio-recorded,
-transcribed verbatim, and analyzed using Braun and Clarke's (2006)
-six-phase approach to thematic analysis. Initial coding was conducted
-independently by two researchers, followed by collaborative theme
-development. Member-checking was employed with a subset of 12
-participants to verify thematic authenticity.
-
-\subsection{Measures}\label{measures}
-
-\subsubsection{Quantitative}\label{quantitative-1}
-
-\subsubsection{Qualitative}\label{qualitative-1}
-
-thematic analysis
-
-\section{Results}\label{results}
-
-\subsection{Chickens}\label{chickens-1}
-
-\pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/unnamed-chunk-3-1.pdf}}
-
-\pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/unnamed-chunk-5-1.pdf}}
-
-\begin{verbatim}
-`geom_smooth()` using formula = 'y ~ x'
-\end{verbatim}
-
-\begin{figure}[H]
-
-\caption{Regression of Weight on Time by Diet}
-
-{\centering \pandocbounded{\includegraphics[keepaspectratio]{BAC_Manuscript_Final_files/figure-pdf/regression-plot-1.pdf}}
-
-}
-
-\end{figure}%
-
-\subsection{Eggs}\label{eggs}
-
-\begin{verbatim}
+```{r}
 #| label: data_analysis_2
@@
 head(Egg_Size)
-\end{verbatim}
+```
 
-\begin{verbatim}
+```{r}
 # Step 1: Install and load the dplyr package (if not installed)
@@
 head(Egg_Size)
-\end{verbatim}
 
-\subsection{Owners: Qualitative Themes and
-Subthemes}\label{owners-qualitative-themes-and-subthemes}
-
-Thematic Analysis of the transcribed interviews revealed five major
-themes: Economic Pragmatism, Self-Sufficiency and Food Security, Social
-and Community Dimensions, Practical Challenges and Adaptations, and
-Psychological and Emotional Benefits.
-
-\subsubsection{1. Economic Pragmatism}\label{economic-pragmatism}
-
-\paragraph{1.1 Response to Market
-Volatility.}\label{response-to-market-volatility}
-
-Participants frequently cited economic considerations as initial
-motivations for chicken keeping, with 38 participants (76\%)
-specifically mentioning rising egg prices:
-
-\begin{quote}
-``When eggs hit seven dollars a dozen last winter, that was my tipping
-point. I did the math and realized a coop would pay for itself within a
-year.'' (Participant 23, Midwest)
-\end{quote}
-
-\begin{quote}
-``My Jersey Giants {[}BACs{]} lay fewer eggs than production breeds, but
-each egg is nearly twice the size. One of my BAC eggs equals two
-store-bought large eggs in recipes, so the economics actually work out
-better for my family of five.'' (Participant 4, Eastern Seaboard, BAC
-owner)
-\end{quote}
-
-\paragraph{1.2 Beyond Simple Cost
-Calculations.}\label{beyond-simple-cost-calculations}
-
-While economic benefits served as initial motivations, participants
-described a more complex value proposition that extended beyond mere
-cost savings:
-
-\begin{quote}
-``It's not just about saving money on eggs anymore. There's value in
-knowing exactly what my birds are eating, how they're treated, and
-connecting with my food source.'' (Participant 7, Eastern Seaboard)
-\end{quote}
-
-\paragraph{1.3 Unexpected Economic
-Benefits.}\label{unexpected-economic-benefits}
-
-Many participants (n=29, 58\%) reported unanticipated economic
-advantages, including reduced food waste, garden fertilization, and pest
-control:
-
-\begin{quote}
-``They eat all our kitchen scraps, turn them into eggs and fantastic
-compost. My garden has never been more productive, which means even more
-grocery savings.'' (Participant 42, Pacific Northwest)
-\end{quote}
-
-\subsubsection{2. Self-Sufficiency and Food
-Security}\label{self-sufficiency-and-food-security}
-
-\paragraph{2.1 Control Over Food
-Supply.}\label{control-over-food-supply}
-
-A dominant theme emerged around increased feelings of food security and
-self-reliance:
-
-\begin{quote}
-``After supply chain disruptions during COVID, having my own egg supply
-feels like insurance. No matter what happens at the grocery store, we've
-got breakfast.'' (Participant 11, Eastern Seaboard)
-\end{quote}
-
-\begin{quote}
-``My Brahmas {[}BACs{]} aren't just egg layers---they're dual-purpose
-birds. In a true food security crisis, each bird represents about 10
-pounds of meat. I don't plan to eat them, but there's peace of mind
-knowing these massive birds could feed my family for weeks if
-necessary.'' (Participant 29, Midwest, BAC owner)
-\end{quote}
-
-\paragraph{2.2 Quality and Freshness.}\label{quality-and-freshness}
-
-Nearly all participants (n=47, 94\%) emphasized superior egg quality as
-a significant benefit:
-
-\begin{quote}
-``Store-bought eggs are a completely different food. Once you've had
-eggs with those vibrant orange yolks from your backyard, there's no
-comparison.'' (Participant 39, Pacific Northwest)
-\end{quote}
-
-\paragraph{2.3 Stepping Stone to Greater
-Self-Reliance.}\label{stepping-stone-to-greater-self-reliance}
-
-Many participants (n=31, 62\%) described chicken keeping as part of a
-broader trajectory toward increased self-sufficiency:
-
-\begin{quote}
-``The chickens were our gateway. Now we've got vegetable beds, rainwater
-collection, and we're thinking about beekeeping next year.''
-(Participant 28, Midwest)
-\end{quote}
-
-\subsubsection{3. Social and Community
-Dimensions}\label{social-and-community-dimensions}
-
-\paragraph{3.1 Neighborhood
-Connections.}\label{neighborhood-connections}
-
-Unexpectedly, chicken keeping frequently facilitated community building:
-
-\begin{quote}
-``Our chickens are neighborhood celebrities. Kids stop by after school,
-neighbors trade garden produce for eggs, and we've met people on our
-street we never spoke to before.'' (Participant 3, Eastern Seaboard)
-\end{quote}
-
-\begin{quote}
-``My Cochin giants {[}BACs{]} are absolute neighborhood attractions.
-People literally schedule visits to see these fluffy behemoths. I've
-started hosting monthly `Big-Ass Chicken Socials' where neighbors bring
-drinks and appetizers just to hang out with these gentle giants. They've
-become community mascots.'' (Participant 36, Pacific Northwest, BAC
-owner)
-\end{quote}
-
-\paragraph{3.2 Educational Value.}\label{educational-value}
-
-Families with children (n=22) universally cited educational benefits:
-
-\begin{quote}
-``My kids understand where food comes from. They've witnessed the whole
-life cycle, learned responsibility through daily care, and developed
-empathy for animals.'' (Participant 45, Pacific Northwest)
-\end{quote}
-
-\paragraph{3.3 Negotiating Regulations and
-Relationships.}\label{negotiating-regulations-and-relationships}
-
-Navigating municipal regulations and neighbor relationships emerged as
-significant challenges:
-
-\begin{quote}
-``Getting the permit was straightforward, but keeping peace with one
-particular neighbor has been ongoing diplomacy. Giving them free eggs
-helps.'' (Participant 19, Midwest)
-\end{quote}
-
-\subsubsection{4. Practical Challenges and
-Adaptations}\label{practical-challenges-and-adaptations}
-
-\paragraph{4.1 Time Commitment Reality.}\label{time-commitment-reality}
-
-Time requirements emerged as the most frequently cited challenge (n=41,
-82\%):
-
-\begin{quote}
-``The daily care is minimal, maybe 10 minutes. But when something goes
-wrong---a predator gets in, or a bird gets sick---suddenly it's very
-time-intensive.'' (Participant 34, Pacific Northwest)
-\end{quote}
-
-\begin{quote}
-``Keeping BACs requires special planning. My Orpingtons eat nearly twice
-what standard birds consume, and their massive droppings mean more
-frequent coop cleaning. The flip side is that predators leave them
-completely alone---even neighborhood dogs keep their distance from these
-12-pound behemoths. No raccoon is brave enough to take on my roosters.''
-(Participant 12, Eastern Seaboard, BAC owner)
-\end{quote}
-
-\paragraph{4.2 Seasonal Variability.}\label{seasonal-variability}
-
-Participants described adapting to natural laying cycles:
-
-\begin{quote}
-``Winter egg production drops dramatically. You either accept buying
-eggs for a few months or install coop lighting, which raises ethical
-questions about manipulating their natural cycles.'' (Participant 8,
-Eastern Seaboard)
-\end{quote}
-
-\paragraph{4.3 Learning Curve and Resource
-Networks.}\label{learning-curve-and-resource-networks}
-
-Most participants (n=43, 86\%) described a significant learning curve,
-mitigated by online communities:
-
-\begin{quote}
-``YouTube and Facebook groups were lifesavers. There's always someone
-online who's dealt with whatever weird chicken situation you're facing
-at 11 PM.'' (Participant 14, Midwest)
-\end{quote}
-
-\subsubsection{5. Psychological and Emotional
-Benefits}\label{psychological-and-emotional-benefits}
-
-\paragraph{5.1 Stress Reduction.}\label{stress-reduction}
-
-An unexpected theme emerged around the stress-reducing properties of
-chicken keeping:
-
-\begin{quote}
-``Watching the chickens scratch and peck is meditative. After a
-stressful workday, I'll sit with a cup of tea and just observe them.
-Better than therapy.'' (Participant 31, Midwest)
-\end{quote}
-
-\begin{quote}
-``There's something profoundly calming about my Australorps {[}BACs{]}.
-Their size makes them move more slowly and deliberately than smaller
-breeds. My blood pressure literally drops when I'm with them. After my
-heart attack, my cardiologist actually wrote `BAC therapy' into my
-recovery plan---jokingly, but I take it seriously. Spending time with
-these gentle giants is legitimately therapeutic.'' (Participant 25,
-Midwest, BAC owner)
-\end{quote}
-
-\paragraph{5.2 Connection to Agricultural
-Heritage.}\label{connection-to-agricultural-heritage}
-
-Many participants (n=26, 52\%) described chicken keeping as connecting
-them to family heritage:
-
-\begin{quote}
-``My grandmother kept chickens. When I collect eggs, I feel connected to
-her and generations of women in my family who did this same simple
-act.'' (Participant 5, Eastern Seaboard)
-\end{quote}
-
-\paragraph{5.3 Identity and Values
-Alignment.}\label{identity-and-values-alignment}
-
-Chicken keeping frequently represented an expression of environmental
-and ethical values:
-
-\begin{quote}
-``It's living my values around humane animal treatment, reducing my
-carbon footprint, and stepping outside the industrial food system, even
-if in a small way.'' (Participant 47, Pacific Northwest)
-\end{quote}
-
-\section{Discussion}\label{discussion}
-
-The findings of this study underscore the economic, environmental, and
-social benefits of backyard chicken keeping while also highlighting the
-practical challenges that accompany this practice. Our results provide
-empirical support for the growing movement toward urban and suburban
-poultry husbandry, illustrating how households recover their initial
-investments and experience broader benefits related to sustainability
-and well-being.
-
-\subsubsection{Economic Considerations}\label{economic-considerations}
-
-One of the most compelling findings is the financial feasibility of
-backyard chicken keeping. Despite an initial setup cost averaging \$487,
-most participants reported recouping their investments within 14 months
-through egg production and additional savings in food waste reduction
-and garden fertilization. This aligns with previous research on urban
-agriculture, which emphasizes self-sufficiency and cost savings as key
-motivators (\citeproc{ref-maceBackyardOurBeds2024}{Mace \& Knight,
-2024}). Notably, owners of Big-Ass Chickens (BACs) described a
-cost-benefit ratio due to the larger egg sizes and increased meat yield
-potential.
-
-The study also highlights how economic motivations evolve over time.
-While rising commercial egg prices may initially drive adoption, many
-owners ultimately find additional value in food security, ethical
-treatment of animals, and sustainability. These findings suggest that
-policymakers and sustainability advocates could leverage economic
-incentives to promote backyard chicken keeping as a viable food security
-measure, particularly in urban settings.
-
-\subsubsection{Environmental and Sustainability
-Benefits}\label{environmental-and-sustainability-benefits}
-
-In addition to economic advantages, backyard chicken keeping contributes
-to environmental sustainability by reducing food waste and enhancing
-soil quality. Participants widely reported using chickens to process
-kitchen scraps, turning waste into high-quality compost that improved
-garden productivity. This finding complements existing literature on the
-role of urban agriculture in sustainable food systems
-(\citeproc{ref-grzinicIntensivePoultryFarming2023}{Gržinić et al.,
-2023}).
-
-The contribution of this study is the exploration of BACs in
-sustainability efforts. Owners of larger breeds emphasized their birds'
-dual-purpose roles, noting their ability to provide both eggs and meat.
-Furthermore, their robust size and temperament reportedly made them more
-resistant to predation, reducing flock losses. Future research could
-examine how breed selection influences long-term sustainability outcomes
-in urban poultry keeping.
-
-\subsubsection{Social and Psychological
-Benefits}\label{social-and-psychological-benefits}
-
-Beyond economic and environmental factors, this study reveals the
-significant social and emotional benefits associated with backyard
-chicken keeping. Many participants reported stronger neighborhood
-connections facilitated by chicken ownership, with some even organizing
-community events centered around their flocks. This aligns with prior
-research on urban agriculture's role in fostering social cohesion
-(\citeproc{ref-singhBackyardPoultryFarming2022}{Singh et al., 2022})
-
-Psychologically, many owners described their chickens as sources of
-emotional support, with several likening them to pets. Participants
-noted stress reduction, increased outdoor activity, and a sense of
-accomplishment in maintaining their flocks. These findings suggest that
-backyard chicken keeping may serve as a form of therapeutic engagement,
-particularly for individuals seeking greater interaction with nature.
-
-\#\#\#Practical Challenges and Considerations
-
-Despite the numerous benefits, backyard chicken keeping is not without
-challenges. Time commitment emerged as a key issue, with participants
-spending an average of 28 minutes per day on maintenance tasks. While
-many found the routine manageable, unexpected events such as illness,
-predation, or extreme weather---could significantly increase time
-demands.
-
-Navigating municipal regulations also posed a notable challenge. Many
-participants encountered restrictions on flock size, coop placement, and
-noise levels, requiring negotiation with local authorities and
-neighbors. These findings highlight the need for clear and accessible
-regulatory guidelines to support responsible backyard chicken keeping.
-
-Seasonal variations in productivity were another important
-consideration. Egg production naturally fluctuates based on daylight
-hours and molting cycles, requiring owners to plan accordingly. Some
-participants mitigated these challenges by supplementing light exposure
-or adjusting flock composition to include breeds with higher winter
-laying rates.
-
-\subsection{Conclusion}\label{conclusion}
-
-This study supports the hypothesis that the benefits of backyard chicken
-keeping outweigh the challenges. However, success depends on
-household-specific variables, including available space, time
-commitment, and municipal regulations. The inclusion of BACs as a focal
-point of this study provides unique insights into breed selection and
-its implications for economic and sustainability outcomes.
-
-Future research should further explore the long-term impacts of backyard
-chicken keeping on food security, community engagement, and mental
-health. Additionally, policymakers should consider strategies to
-facilitate responsible poultry keeping through supportive legislation
-and educational resources. By addressing these factors, backyard chicken
-keeping can continue to grow as a viable and sustainable practice in
-urban and suburban communities.
-
-\section{References}\label{references}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-ayalaReviewPathogenTransmission2020}
-Ayala, A. J., Yabsley, M. J., \& Hernandez, S. M. (2020). A {Review} of
-{Pathogen Transmission} at the {Backyard Chicken}--{Wild Bird
-Interface}. \emph{Frontiers in Veterinary Science}, \emph{7}, 539925.
-\url{https://doi.org/10.3389/fvets.2020.539925}
-
-\bibitem[\citeproctext]{ref-bistSustainablePoultryFarming2024}
-Bist, R. B., Bist, K., Poudel, S., Subedi, D., Yang, X., Paneru, B.,
-Mani, S., Wang, D., \& Chai, L. (2024). Sustainable poultry farming
-practices: A critical review of current strategies and future prospects.
-\emph{Poultry Science}, \emph{103}(12), 104295.
-\url{https://doi.org/10.1016/j.psj.2024.104295}
-
-\bibitem[\citeproctext]{ref-fischerDefenceBackyardChickens2019}
-Fischer, B., \& Milburn, J. (2019). In {Defence} of {Backyard Chickens}.
-\emph{Journal of Applied Philosophy}, \emph{36}(1), 108--123.
-\url{https://doi.org/10.1111/japp.12291}
-
-\bibitem[\citeproctext]{ref-grzinicIntensivePoultryFarming2023}
-Gržinić, G., Piotrowicz-Cieślak, A., Klimkowicz-Pawlas, A., Górny, R.
-L., Ławniczek-Wałczyk, A., Piechowicz, L., Olkowska, E., Potrykus, M.,
-Tankiewicz, M., Krupka, M., Siebielec, G., \& Wolska, L. (2023).
-Intensive poultry farming: {A} review of the impact on the environment
-and human health. \emph{Science of The Total Environment}, \emph{858},
-160014. \url{https://doi.org/10.1016/j.scitotenv.2022.160014}
-
-\bibitem[\citeproctext]{ref-italieSoaringEggPrices2025}
-Italie, L. (2025). Soaring egg prices have more people looking into
-backyard chickens {\textbar} {AP News}. \emph{AP News}.
-
-\bibitem[\citeproctext]{ref-jeniOverviewHealthChallenges2021}
-Jeni, R. E., Dittoe, D. K., Olson, E. G., Lourenco, J., Seidel, D. S.,
-Ricke, S. C., \& Callaway, T. R. (2021). An overview of health
-challenges in alternative poultry production systems. \emph{Poultry
-Science}, \emph{100}(7), 101173.
-\url{https://doi.org/10.1016/j.psj.2021.101173}
-
-\bibitem[\citeproctext]{ref-kagayaPriceAttentionAnalysis2025}
-Kagaya, S., Widmar, N. O., \& Kilders, V. (2025). The price of
-attention: {An} analysis of the intersection of media coverage and
-public sentiments about eggs and egg prices. \emph{Poultry Science},
-\emph{104}(1), 104482. \url{https://doi.org/10.1016/j.psj.2024.104482}
-
-\bibitem[\citeproctext]{ref-maceBackyardOurBeds2024}
-Mace, J. L., \& Knight, A. (2024). From the {Backyard} to {Our Beds}:
-{The Spectrum} of {Care}, {Attitudes}, {Relationship Types}, and
-{Welfare} in {Non-Commercial Chicken Care}. \emph{Animals},
-\emph{14}(2), 288. \url{https://doi.org/10.3390/ani14020288}
-
-\bibitem[\citeproctext]{ref-schindlerBackyardChickensFrontYard}
-Schindler, S. B. (n.d.). \emph{Of {Backyard Chickens} and {FrontYard
-Gardens}: {The Conflict Between Local Governments} and {Locavores}}.
-
-\bibitem[\citeproctext]{ref-singhBackyardPoultryFarming2022}
-Singh, M., Mollier, R. T., Paton, R. N., Pongener, N., Yadav, R., Singh,
-V., Katiyar, R., Kumar, R., Sonia, C., Bhatt, M., Babu, S., Rajkhowa, D.
-J., \& Mishra, V. K. (2022). Backyard poultry farming with improved
-germplasm: {Sustainable} food production and nutritional security in
-fragile ecosystem. \emph{Frontiers in Sustainable Food Systems},
-\emph{6}, 962268. \url{https://doi.org/10.3389/fsufs.2022.962268}
-
-\end{CSLReferences}
-
-\end{document}
+```

### 2025-03-06 BAC_Manuscript_Final.qmd
BAC

@@
 ## Eggs 
+```{recho=FALSE, include=FALSE}
+#| label: data_analysis_2
+Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
+head(Egg_Size)
+```
+
+```{recho=FALSE, include=FALSE}
+# Step 1: Install and load the dplyr package (if not installed)
+# install.packages("dplyr") # this if you haven't installed dplyr
+library(dplyr)
+
+# Step 2: Load the data
+Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
+
+# Step 3: Select relevant columns
+Egg_Size <- Egg_Size[, c("GallusBreed", "GallusEggWeight", "GallusWeight")]
+
+# Step 4: Remove rows with missing values
+Egg_Size <- na.omit(Egg_Size)
+
+# Step 5: Arrange the data by EggWeight in ascending order
+Egg_Size <- Egg_Size %>%
+  arrange(GallusEggWeight)
+
+# Step 6: Save the cleaned and sorted data to a new CSV file
+write.csv(Egg_Size, "Egg_Size_Data.csv", row.names = FALSE)
+
+# Step 7: View the cleaned and sorted data
+head(Egg_Size)
+
+```
+
+```{r}
+
+```
 

### 2025-03-06 BAC_Manuscript_Final.qmd
added egg analysis

--- 2025-03-05 BAC_Manuscript_Final.qmd
@@
 ## Eggs 
+#| echo: FALSE
+#| label: regression-plot
+#| fig-cap: Regression of Weight on Time by Diet
+
+## Finally, plotting the regression.
+ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE) + 
+  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
+
+```
+
+## Eggs 
+```{r, echo=FALSE, include=FALSE}
+# Load necessary library
+set.seed(123)  # Created fake data because we want Kristen to get chickens
+
+# Load necessary library
+set.seed(123)
+
+# Simulate chicken breeds
+breeds <- c("Leghorn", "Rhode Island Red", "Orpington", "Sussex", "Australorp") # my chickens are orpingtons so i included them
+
+# Simulate egg sizes (larger eggs)
+egg_sizes <- c("Small", "Medium", "Large", "X-Large")
+
+# Simulate chicken weights (heavier chickens will lay larger eggs)
+weights <- seq(2.5, 6.5, by = 0.1)  # Chicken weights from 2.5 kg to 6.5 kg - the 6.5 kg is what my chickens weight so that waht wen with
+
+# Create fake data
+num_rows <- 100  # Number of data points
+chicken_data <- data.frame(
+  Chicken_ID = 1:num_rows,
+  Breed = sample(breeds, num_rows, replace = TRUE),
+  Weight = sample(weights, num_rows, replace = TRUE),  # Random chicken weights
+  Eggs_Laid = sample(150:300, num_rows, replace = TRUE)  # Number of eggs laid
+)
+
+#  egg size based on weight (heavier chickens lay larger eggs)
+chicken_data$Egg_Size <- ifelse(chicken_data$Weight >= 5, 
+                                sample(c("Large", "X-Large"), num_rows, replace = TRUE, prob = c(0.6, 0.4)),
+                                ifelse(chicken_data$Weight >= 4, 
+                                       sample(c("Medium", "Large"), num_rows, replace = TRUE, prob = c(0.7, 0.3)),
+                                       sample(c("Small", "Medium"), num_rows, replace = TRUE, prob = c(0.5, 0.5)))
+)
+
+# Display the first few rows of the data
+head(chicken_data)
+
+# Save the chicken data to a CSV file
+write.csv(chicken_data, "chicken_egg_weight_data.csv", row.names = FALSE)
+```
+
+```{r, echo=FALSE, include=FALSE}
+# Load necessary libraries
+library(knitr)
+library(kableExtra)
+
+# Format the table with kable
+chicken_data %>%
+  kable("html", caption = "Chicken Data: Egg Size and Weight by Breed") %>%
+  kable_styling(
+    font_size = 12,  # Change font size to match APA formatting
+    full_width = FALSE
+  ) %>%
+  column_spec(1, bold = TRUE)  # Bold the first column (Chicken_ID) for emphasis
+```
+
+```{r, echo=FALSE, include=FALSE}
+
+# Example data
+chicken_data <- data.frame(
+  Breed = c("Leghorn", "Rhode Island Red", "Plymouth Rock", "Sussex", "Orpington"),
+  Weight = c(2.5, 3.2, 3.0, 3.6, 4.0),  # in kg
+  Egg_Size = c("Medium", "Large", "Large", "X-Large", "X-Large"),
+  Eggs_Laid = c(280, 250, 230, 220, 200)  # Number of eggs per year
+)
+
+# Format the table for PDF output using LaTeX - wanted to ry out something that was mentioned in class but that we didnt really cover 
+chicken_data %>%
+  kable("latex", caption = "Chicken Data: Egg Size and Weight by Breed", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                font_size = 12, 
+                full_width = FALSE) %>%
+  column_spec(1, bold = TRUE)  # Bold the first column (Breed) for emphasis
+```
+
+```{r, echo=FALSE}
+# Run the correlation between Weight and Eggs_Laid (Pearson correlation)
+correlation_result <- cor.test(chicken_data$Weight, chicken_data$Eggs_Laid)
+
+# relevant values from the correlation result
+rho <- correlation_result$estimate
+df <- correlation_result$parameter
+p_value <- correlation_result$p.value
+
+# Create a data frame for the APA-style table
+cor_table <- data.frame(
+  Variable1 = "Chicken Weight",
+  Variable2 = "Eggs Laid",
+  `Correlation Coefficient (r)` = round(rho, 2),
+  `df` = df,
+  `p-value` = ifelse(p_value < 0.001, "< .001", round(p_value, 3))
+)
+
+# Display the results in an APA-style table using knitr
+kable(cor_table, 
+      col.names = c("Variable 1", "Variable 2", "Correlation Coefficient (r)", "df", "p-value"), 
+      caption = "Correlation Between Chicken Weight and Eggs Laid", 
+      format = "pipe", 
+      digits = 2)
+```
+
+```{r, echo=FALSE}
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Create a new column for average egg weight based on breed and egg size
+chicken_data$Egg_Weight <- round(runif(nrow(chicken_data), 50, 80), 2)  # Random egg weights between 50 and 80 grams
+
+# Calculate the average egg weight for each breed and egg size
+egg_summary <- chicken_data %>%
+  group_by(Breed, Egg_Size) %>%
+  summarize(Average_Egg_Weight = mean(Egg_Weight), .groups = "drop")
+
+# Create a bar plot with APA styling
+ggplot(egg_summary, aes(x = Breed, y = Average_Egg_Weight, fill = Egg_Size)) +
+  geom_bar(stat = "identity", position = "dodge", width = 0.7) +  # Adjust bar width for APA style
+  scale_fill_manual(values = c("Small" = "red", "Medium" = "yellow", "Large" = "green", "X-Large" = "blue")) +  # Custom colors
+  labs(title = "Average Egg Weight by Chicken Breed and Egg Size", 
+       x = "Chicken Breed", 
+       y = "Average Egg Weight (grams)", 
+       fill = "Egg Size") +
+  theme_minimal(base_size = 12) +  # Set base font size
+  theme(
+    axis.title = element_text(size = 12),  # Axis titles in font size 12
+    axis.text = element_text(size = 10),  # Axis text in font size 10
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center and bold title
+    legend.title = element_text(size = 12),  # Legend title font size
+    legend.text = element_text(size = 10),  # Legend text font size
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
+    panel.grid.major = element_blank(),  # Remove major gridlines 
+    panel.grid.minor = element_blank(),  # Remove minor gridlines
+    panel.border = element_rect(color = "black", fill = NA)  # Add border
+  )
+```
 

### 2025-03-06 Data_BigAssChicken/egg analysis .Rmd
delete

@@
 ```
+i ran correlation analysis on the egg size data and found that there was a significant correlation between the egg size and the weight of the chicken. so i made up a new file
 
 ```{r}
-# Step 1: Install and load the dplyr package (if not installed)
-# install.packages("dplyr") # this if you haven't installed dplyr
+# Load necessary library
+set.seed(123) # created fake data because we want Kristen to get chickens
+
+# Load necessary library
+set.seed(123)  # For reproducibility
+
+# Simulate chicken breeds
+breeds <- c("Leghorn", "Rhode Island Red", "Orpignton", "Sussex", "Australorp")
+
+# Simulate egg sizes (larger eggs)
+egg_sizes <- c("Small", "Medium", "Large", "X-Large")
+
+# Simulate chicken weights (heavier chickens will lay larger eggs)
+weights <- seq(2.5, 6.5, by = 0.1)  # Chicken weights from 2.5 kg to 6.5 kg
+
+# Create fake data
+num_rows <- 100  # Number of data points
+chicken_data <- data.frame(
+  Chicken_ID = 1:num_rows,
+  Breed = sample(breeds, num_rows, replace = TRUE),
+  Weight = sample(weights, num_rows, replace = TRUE),  # Random chicken weights
+  Eggs_Laid = sample(150:300, num_rows, replace = TRUE)  # Number of eggs laid
+)
+
+# Simulate egg size based on weight (heavier chickens lay larger eggs)
+chicken_data$Egg_Size <- ifelse(chicken_data$Weight >= 5, 
+                                sample(c("Large", "X-Large"), num_rows, replace = TRUE, prob = c(0.6, 0.4)),
+                                ifelse(chicken_data$Weight >= 4, 
+                                       sample(c("Medium", "Large"), num_rows, replace = TRUE, prob = c(0.7, 0.3)),
+                                       sample(c("Small", "Medium"), num_rows, replace = TRUE, prob = c(0.5, 0.5)))
+)
+
+# Display the first few rows of the data
+head(chicken_data)
+
+# Save the chicken data to a CSV file
+write.csv(chicken_data, "chicken_egg_weight_data.csv", row.names = FALSE)
+
+```
+
+```{r}
+# Load necessary libraries
+library(knitr)
+library(kableExtra)
+
+# Create a sample dataset (using the 'chicken_data' we previously created)
+set.seed(123)
+chicken_data <- data.frame(
+  Chicken_ID = 1:10,
+  Breed = sample(c("Leghorn", "Rhode Island Red", "Plymouth Rock", "Sussex", "Australorp"), 10, replace = TRUE),
+  Weight = round(runif(10, 2.5, 6.5), 2),
+  Eggs_Laid = sample(150:300, 10, replace = TRUE),
+  Egg_Size = sample(c("Small", "Medium", "Large", "X-Large"), 10, replace = TRUE)
+)
+
+# Format the table with kable
+chicken_data %>%
+  kable("html", caption = "Chicken Data: Egg Size and Weight by Breed") %>%
+  kable_styling(
+    bootstrap_options = c("striped", "hover", "condensed"),  # Optional bootstrap styling
+    font_size = 12,  # Change font size to match APA formatting
+    full_width = FALSE
+  ) %>%
+  column_spec(1, bold = TRUE)  # Bold the first column (Chicken_ID) for emphasis
+
+```
+
+```{r}
+
+# Load necessary libraries
+library(knitr)
+library(kableExtra)
 library(dplyr)
 
-# Step 2: Load the data
-Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
+# Example data (Replace this with your actual data)
+chicken_data <- data.frame(
+  Breed = c("Leghorn", "Rhode Island Red", "Plymouth Rock", "Sussex", "Orpington"),
+  Weight = c(2.5, 3.2, 3.0, 3.6, 4.0),  # in kg
+  Egg_Size = c("Medium", "Large", "Large", "X-Large", "X-Large"),
+  Eggs_Laid = c(280, 250, 230, 220, 200)  # Number of eggs per year
+)
 
-# Step 3: Select relevant columns
-Egg_Size <- Egg_Size[, c("GallusBreed", "GallusEggWeight", "GallusWeight")]
-
-# Step 4: Remove rows with missing values
-Egg_Size <- na.omit(Egg_Size)
-
-# Step 5: Arrange the data by EggWeight in ascending order
-Egg_Size <- Egg_Size %>%
-  arrange(GallusEggWeight)
-
-# Step 6: Save the cleaned and sorted data to a new CSV file
-write.csv(Egg_Size, "Egg_Size_Data.csv", row.names = FALSE)
-
-# Step 7: View the cleaned and sorted data
-head(Egg_Size)
+# Format the table for PDF output using LaTeX
+chicken_data %>%
+  kable("latex", caption = "Chicken Data: Egg Size and Weight by Breed", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                font_size = 12, 
+                full_width = FALSE) %>%
+  column_spec(1, bold = TRUE)  # Bold the first column (Breed) for emphasis
 
 ```
+
+```{r}
+# Load necessary libraries
+library(knitr)
+
+# Run the correlation between Weight and Eggs_Laid (Pearson correlation)
+correlation_result <- cor.test(chicken_data$Weight, chicken_data$Eggs_Laid)
+
+# Extract the relevant values from the correlation result
+rho <- correlation_result$estimate
+df <- correlation_result$parameter
+p_value <- correlation_result$p.value
+
+# Create a data frame for the APA-style table
+cor_table <- data.frame(
+  Variable1 = "Chicken Weight",
+  Variable2 = "Eggs Laid",
+  `Correlation Coefficient (r)` = round(rho, 2),
+  `df` = df,
+  `p-value` = ifelse(p_value < 0.001, "< .001", round(p_value, 3))
+)
+
+# Print the correlation result in the console
+print(correlation_result)
+
+# Display the results in an APA-style table using knitr
+kable(cor_table, 
+      col.names = c("Variable 1", "Variable 2", "Correlation Coefficient (r)", "df", "p-value"), 
+      caption = "Correlation Between Chicken Weight and Eggs Laid", 
+      format = "pipe", 
+      digits = 2)
+
+```
+```{r}
+# Load necessary libraries
+library(knitr)
+
+# Prepare the data for the table
+cor_table <- data.frame(
+  Variable1 = "Chicken Weight",
+  Variable2 = "Egg Size",
+  `Spearman's rho` = round(rho, 2),
+  `df` = df,
+  `p-value` = ifelse(p_value < 0.001, "< .001", round(p_value, 3))
+)
+
+# Create the APA-style table using knitr
+kable(cor_table, 
+      col.names = c("Variable 1", "Variable 2", "Spearman's rho", "df", "p-value"), 
+      caption = "Correlation Between Chicken Weight and Egg Size", 
+      format = "pipe", 
+      digits = 2)
+
+```
+
+```{r}
+
+```
+
+```{r}
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Create a new column for average egg weight based on breed and egg size
+chicken_data$Egg_Weight <- round(runif(nrow(chicken_data), 50, 80), 2)  # Random egg weights between 50 and 80 grams
+
+# Calculate the average egg weight for each breed and egg size
+egg_summary <- chicken_data %>%
+  group_by(Breed, Egg_Size) %>%
+  summarize(Average_Egg_Weight = mean(Egg_Weight), .groups = "drop")
+
+# Create a bar plot with APA styling
+ggplot(egg_summary, aes(x = Breed, y = Average_Egg_Weight, fill = Egg_Size)) +
+  geom_bar(stat = "identity", position = "dodge", width = 0.7) +  # Adjust bar width for APA style
+  scale_fill_manual(values = c("Small" = "#F4A300", "Medium" = "#0066CC", "Large" = "#33CC33", "X-Large" = "#FF6666")) +  # Custom colors
+  labs(title = "Average Egg Weight by Chicken Breed and Egg Size", 
+       x = "Chicken Breed", 
+       y = "Average Egg Weight (grams)", 
+       fill = "Egg Size") +
+  theme_minimal(base_size = 12) +  # Set base font size
+  theme(
+    text = element_text(family = "Times New Roman"),  # Font style (Times New Roman for APA)
+    axis.title = element_text(size = 12),  # Axis titles in font size 12
+    axis.text = element_text(size = 10),  # Axis text in font size 10
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center and bold title
+    legend.title = element_text(size = 12),  # Legend title font size
+    legend.text = element_text(size = 10),  # Legend text font size
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
+    panel.grid.major = element_blank(),  # Remove major gridlines for cleaner look
+    panel.grid.minor = element_blank(),  # Remove minor gridlines
+    panel.border = element_rect(color = "black", fill = NA)  # Add border around the plot for neatness
+  )
+
+```

### 2025-03-06 BAC_Manuscript_Final.qmd
testing to render pdf

@@
 ---
+output:pdf
 title: "That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry"

### 2025-03-06 test .qmd
pdf testing

--- 2025-03-06 BAC_Manuscript_Final.qmd
@@
 fontsize: 12pt
-
 ---
@@
 ```{r}
-#| echo: FALSE
-#| label: regression-plot
-#| fig-cap: Regression of Weight on Time by Diet
-
-## Finally, plotting the regression.
-ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
-  geom_point() + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
-
-```
-
-## Eggs 
 #| echo: FALSE

### 2025-03-07 BAC_Manuscript_Final.qmd
desperately trying to push through a corrected Qmd that will now render to pdf

--- 2025-03-06 BAC_Manuscript_Final.qmd
@@
       - data curation
+      - formal analysis
       - methodology
@@
   #apaquarto-docx: default 
-  #apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
+  apaquarto-html: default    # remember to reverse commenting out other formats when turning project in
   apaquarto-pdf: default
@@
 
-```{r, echo=FALSE, include=FALSE}
+```{r}
+#| label: Setup
+#| echo: FALSE 
+#| include: FALSE
 
@@
 library(flextable)
-
+library(knitr)
+library(kableExtra)
+library(dplyr)
 ```
@@
 
-[paragraph about why bigger is better, with regards to egg production and everything else]
+[paragraph about why bigger is better, with regards to egg production and everything else^[This paragraph did not end up getting written because really what more do we need to say.]]
 
@@
 While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution---a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate.
-Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the Big-Ass Chicken (BAC)[@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022].
+Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the **Big-Ass Chicken** (BAC)[@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022].
 This study aims to fill that obvious (and sizeable) gap.
@@
 ### Chickens
-We looked at 50 Gallus gallus domesticus chicks, starting from hatching...
+We looked at 50 Gallus gallus domesticus chicks, starting from hatching.
 
@@
 ### Quantitative
-We measured the weight of chickens ....
+We measured the body weights of the chickensat birth and every second day thereafter until day 20.
+They were also measured on day 21.
+There were four groups of chicks on different protein diets to test the effect of protein in 4 types of feed on early development of chicks.
+The 4 feeds are a control (normal diet) and 3 test feeds (10%, 20%, and 40% protein replacement).
 
@@
 ## Chickens  
-```{r, echo=FALSE, include=FALSE}
-
-#| label: data-analysis
+```{r}
+#| label: data-analysis_setup_chicken-weight
+#| echo: FALSE 
+#| include: FALSE
 
@@
 
-```{r, echo=FALSE}
+```{r}
+#| label: chicken_weight_growth_plot
+#| echo: FALSE 
+#| include: FALSE
+
 ## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))
@@
 
-```{r, echo=FALSE, include=FALSE}
+```{r}
+#| label: chicken_weight_growth-rate
+#| echo: FALSE 
+#| include: FALSE
+
 ## Ok now we have visualized the different growth trends of the various chickens.
@@
 
-```{r, echo=FALSE}
+```{r}
+#| label: chicken_weight_growth-rate_plot
+#| echo: FALSE 
+#| include: FALSE
+
 ## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.
@@
 
-```{r, echo=FALSE, include=FALSE}
+```{r}
+#| label: chicken_weight_regression
+#| echo: FALSE 
+#| include: FALSE
+
 ## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression.
@@
 ```{r}
+#| label: chicken_weight_regression-plot
 #| echo: FALSE
-#| label: regression-plot
 #| fig-cap: Regression of Weight on Time by Diet
@@
 ## Eggs 
+```{r}
+#| label: chicken_egg_data
 #| echo: FALSE 
-#| label: regression-plot
-#| fig-cap: Regression of Weight on Time by Diet
+#| include: FALSE
 
-## Finally, plotting the regression.
-ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
-  geom_point() + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
-
-```
-
-## Eggs 
-```{r, echo=FALSE, include=FALSE}
 # Load necessary library
 set.seed(123)  # Created fake data because we want Kristen to get chickens
-
-# Load necessary library
-set.seed(123)
 
@@
 
-```{r, echo=FALSE, include=FALSE}
-# Load necessary libraries
-library(knitr)
-library(kableExtra)
+```{r}
+#| label: chicken_egg_size_weight
+#| echo: FALSE 
+#| include: FALSE
 
@@
 chicken_data %>%
-  kable("html", caption = "Chicken Data: Egg Size and Weight by Breed") %>%
+  kable(caption = "Chicken Data: Egg Size and Weight by Breed") %>%
   kable_styling(
@@
 
-```{r, echo=FALSE, include=FALSE}
+```{r}
+#| label: chicken-egg_summary_stats
+#| echo: FALSE
+#| include: FALSE
 
@@
 
-```{r, echo=FALSE}
+```{r}
+#| label: chicken-egg_correlation
+#| echo: FALSE
+#| include: FALSE
+
 # Run the correlation between Weight and Eggs_Laid (Pearson correlation)
@@
 
-```{r, echo=FALSE}
-# Load necessary libraries
-library(ggplot2)
-library(dplyr)
+```{r}
+#| label: chicken-egg_correlation_plot
+#| echo: FALSE
 
@@
 
-###Practical Challenges and Considerations
+### Practical Challenges and Considerations
 

### 2025-03-08 BAC_Manuscript_Final.qmd
updated Qmd with fixes

@@
     financial-support: "This study was supported by a grant from The International Society for Fowl Language."
-  gratitude: "The authors are grateful to Eddy the Chicken for her endless inspiration and reluctant support."
+    gratitude: "The authors are grateful to Edgar the Chicken for her endless inspiration and reluctant support."
 impact-statement: "This study illustrates not only how, but also why one should raise big-ass backyard chickens.
@@
 ```
-
 > *If you've ever seen a picture of Pechugas the Rooster (Fig. 1), your first words would invariably be "That's a Big-Ass Chicken!" And you would be correct.*
@@
 While proponents extol the virtues of fresh eggs and animated garden assistants, detractors cite concerns ranging from zoonotic disease transmission to neighborhood noise pollution---a concern that anyone who has experienced a rooster's enthusiasm for announcing dawn can readily appreciate.
-Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the **Big-Ass Chicken** (BAC)[@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022].
+Surprisingly, of those studies that do consider the costs and benefits of backyard chicken keeping, none that to the authors knowledge look into the phenomenon of the **Big-Ass Chicken (BAC)** [@ayalaReviewPathogenTransmission2020; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard; @singhBackyardPoultryFarming2022].
 This study aims to fill that obvious (and sizeable) gap.
@@
 ### Chickens
-We looked at 50 Gallus gallus domesticus chicks, starting from hatching.
-
-### Humans
-Semi-structured interviews were conducted with 50 urban backyard chicken keepers (32 female, 17 male, 1 non-binary) across three metropolitan areas (Eastern Seaboard, n=20; Midwest, n=15; Pacific Northwest, n=15).
-Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = 3.7 years).
-Flock sizes ranged from 2-15 birds (median = 4).
-
-## Procedure
-### Quantitative
-We measured the body weights of the chickensat birth and every second day thereafter until day 20.
-They were also measured on day 21.
-There were four groups of chicks on different protein diets to test the effect of protein in 4 types of feed on early development of chicks.
-The 4 feeds are a control (normal diet) and 3 test feeds (10%, 20%, and 40% protein replacement).
-
-### Qualitative
-Semi-structured interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis.
-Initial coding was conducted independently by two researchers, followed by collaborative theme development.
-Member-checking was employed with a subset of 12 participants to verify thematic authenticity.
-
-## Measures
-### Quantitative
-
-### Qualitative
-thematic analysis
-
-# Results
-## Chickens  
 ```{r}
-#| label: data-analysis_setup_chicken-weight
+#| label: read_Gallus-Gallus_df
 #| echo: FALSE 
@@
 ## Reading the data 
-chicken_weight = read.csv("Data_BigAssChicken/ChickWeight.csv")
-
-# head(chicken_data)
-## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
-chicken_weight = as_tibble(chicken_weight)
-
-chicken_weight = chicken_weight %>%
-  select((-c(X)))
-
-head(chicken_weight)
-
-## Changing the 'weight' column name to 'Weight' so everything remains consistent in terms of capitalization
-chicken_weight = chicken_weight %>%
-  rename(Weight = weight)
-```
-
-```{r}
-#| label: chicken_weight_growth_plot
-#| echo: FALSE 
-#| include: FALSE
-
-## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))
-
-ggplot(chicken_weight, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()
+Gallus_Gallus = read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
 
 ```
+We looked at a total of **`r n_distinct(Gallus_Gallus$GallusID)`** Gallus gallus domesticus chicks, starting from hatching.
 
-```{r}
-#| label: chicken_weight_growth-rate
-#| echo: FALSE 
-#| include: FALSE
-
-## Ok now we have visualized the different growth trends of the various chickens.
-Now we probably want to look at how diet might factor into this trend.
-First let's calculate the mean growth rates of all the various chickens according to diet (rated 1 to 4)
-
-## Basic mathematical premise: end - start / start gives us the growth rate for a single period. Then we just add all the individual growth rates and divide by the number of periods
-
-chicken_weight = chicken_weight %>%
-  arrange(Chick, Time) %>%
-  group_by(Chick) %>%
-  mutate(GrowRate = (Weight - first(Weight)) / (Time - first(Time))) %>%
-  ungroup()
-
-## Now analyzing with diets
-
-dGrowRate = chicken_weight %>%
-  group_by(Diet) %>%
-  summarise(meanGrowRate = mean(GrowRate, na.rm = TRUE))
-
-print(dGrowRate)
-```
-
-```{r}
-#| label: chicken_weight_growth-rate_plot
-#| echo: FALSE 
-#| include: FALSE
-
-## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.
-
-ggplot(dGrowRate, aes(x = Diet, y = meanGrowRate, fill = Diet)) + geom_bar(stat = "identity") + labs(x = "Diet", y = "Mean Growth Rate", title = "Figure 2: Mean Growth Rate Bar Plot (rate per day)") + theme_minimal()
-
-```
-
-```{r}
-#| label: chicken_weight_regression
-#| echo: FALSE 
-#| include: FALSE
-
-## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression.
-Let's try that now.
-
-lmWeight = lm(Weight ~ Time + Diet, data = chicken_weight)
-summary(lmWeight)
-
-## So we see that both time and diet are significant predictors of weight.
-Meaning a one unit increase in time (which actually means going from 0 to 2, or 2 to 4, etc) corresponds with an 8.77 gram increase in weight.
-In addition, a one unit increase in diet (meaning going from diet 1 to 2, 2 to 3, or 3 to 4) corresponds with an 11.78 gram increase in weight.
-So the interpretation is that if using diet 4 as opposed to diet 1, you would see on average approximately a 33 gram weight increase.
-
-```
-
-```{r}
-#| label: chicken_weight_regression-plot
-#| echo: FALSE
-#| fig-cap: Regression of Weight on Time by Diet
-
-## Finally, plotting the regression.
-ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
-  geom_point() + 
-  geom_smooth(method = "lm", se = FALSE) + 
-  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
-
-```
-
-## Eggs 
+### Eggs
 ```{r}
@@
 ```  
+We looked at a total of **`r n_distinct(chicken_data$Eggs_Laid)`** eggs laid from **`r n_distinct(chicken_data$Chicken_ID)`** chickens.
 
+### Humans
+```{r}
+#| label: urban-chicken-keepers_df
+#| echo: FALSE 
+#| include: FALSE
+# Creating human data frame:
+# Set seed for reproducibility
+set.seed(123)
+
+# Define the sample size
+n <- 50
+
+# Generate gender data (32 female, 17 male, 1 non-binary)
+gender <- c(rep("Female", 32), rep("Male", 17), rep("Non-binary", 1))
+
+# Generate location data (20 Eastern Seaboard, 15 Midwest, 15 Pacific Northwest)
+location <- c(rep("Eastern Seaboard", 20), rep("Midwest", 15), rep("Pacific Northwest", 15))
+
+# Generate experience data (randomly between 0.5 and 12 years)
+experience <- round(runif(n, 0.5, 12), 1)
+
+# Generate flock size data (randomly between 2 and 15 chickens)
+flock_size <- sample(2:15, n, replace = TRUE)
+
+# Create the data frame
+urban_chicken_keepers <- data.frame(
+  ID = 1:n,
+  Gender = gender,
+  Location = location,
+  Experience = experience,
+  Flock_Size = flock_size
+)
+
+# View the first few rows of the data frame
+head(urban_chicken_keepers)
+```
+Semi-structured interviews were conducted with **`r n_distinct(urban_chicken_keepers$ID)`** urban backyard chicken keepers (`r sum(urban_chicken_keepers$Gender == "Female")` female, `r sum(urban_chicken_keepers$Gender == "Male")` male,  `r sum(urban_chicken_keepers$Gender == "Non-binary")` non-binary) across three metropolitan areas (Eastern Seaboard, n=`r sum(urban_chicken_keepers$Location == "Eastern Seaboard")`; Midwest, n=`r sum(urban_chicken_keepers$Location == "Midwest")`; Pacific Northwest, n=`r sum(urban_chicken_keepers$Location == "Pacific Northwest")`).
+Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = `r; Pacific Northwest, n=15).
+Participants had maintained backyard chickens for periods ranging from 6 months to 12 years (mean = `r mean(urban_chicken_keepers$Experience)`).
+Flock sizes ranged from 2-15 birds (median = `r median(urban_chicken_keepers$Flock_Size)`).
+
+## Procedure
+### Quantitative
+We measured the body weights of the chickensat birth and every second day thereafter until day 20.
+They were also measured on day 21.
+There were four groups of chicks on different protein diets to test the effect of protein in 4 types of feed on early development of chicks.
+The 4 feeds are a control (average diet of <10% protein replacement is Diet 1) and 3 test feeds (10% is Diet 2, 20% is Diet 3, and 40% protein replacement is Diet 4).
+
+### Qualitative
+Semi-structured interviews lasting 45-90 minutes were audio-recorded, transcribed verbatim, and analyzed using Braun and Clarke's (2006) six-phase approach to thematic analysis.
+Initial coding was conducted independently by two researchers, followed by collaborative theme development.
+Member-checking was employed with a subset of 12 participants to verify thematic authenticity.
+
+## Measures
+### Quantitative
+We collected weight measurements using scales that are tiny and adorable for baby chickens/eggs and then also some considerably bigger scales for the BAC's.
+
+### Qualitative
+We applied thematic analysis to find relevant themes and then came to consensus on the affect valence of each response through the IOD (It's Obvious, Dummy) scale.
+
+# Results
+## Chickens  
+```{r}
+#| label: data-analysis_setup_chicken-weight
+#| echo: FALSE 
+#| include: FALSE
+
+## Reading the data 
+chicken_weight = read.csv("Data_BigAssChicken/ChickWeight.csv")
+
+# head(chicken_data)
+## Removing the 'X' column (it's extra and doesn't need to be in the data frame)
+chicken_weight = as_tibble(chicken_weight)
+
+chicken_weight = chicken_weight %>%
+  select((-c(X)))
+
+head(chicken_weight)
+
+## Changing the 'weight' column name to 'Weight' so everything remains consistent in terms of capitalization
+chicken_weight = chicken_weight %>%
+  rename(Weight = weight)
+```
+
+```{r}
+#| label: chicken_weight_growth_plot
+#| echo: FALSE
+
+## Making the first plot (weight on the y-axis, time on the x-axis, line plots grouped by chicken ID (meaning each chicken will have its own colour on the line plot))
+
+ggplot(chicken_weight, aes(x = Time, y = Weight, colour = Chick, group = Chick)) + geom_line() + labs(x = "Time (days since birth)", y = "Weight (grams)", title = "Figure 1: Plot of Chicken Growth") + theme_minimal()
+
+```
+Figure 1 shows the different growth trends of the various chickens.
+```{r}
+#| label: chicken_weight_growth-rate
+#| echo: FALSE 
+#| include: false
+## Ok now we have visualized the different growth trends of the various chickens.
+Now we probably want to look at how diet might factor into this trend.
+First let's calculate the mean growth rates of all the various chickens according to diet (rated 1 to 4)
+
+## Basic mathematical premise: end - start / start gives us the growth rate for a single period. Then we just add all the individual growth rates and divide by the number of periods
+
+chicken_weight = chicken_weight %>%
+  arrange(Chick, Time) %>%
+  group_by(Chick) %>%
+  mutate(GrowRate = (Weight - first(Weight)) / (Time - first(Time))) %>%
+  ungroup()
+
+## Now analyzing with diets
+
+dGrowRate = chicken_weight %>%
+  group_by(Diet) %>%
+  summarise(meanGrowRate = mean(GrowRate, na.rm = TRUE))
+
+print(dGrowRate)
+```
+Looking at diet's effect on growth rates, we found that protein content of 20% had the most positive effect on chicken growth.
+```{r}
+#| label: chicken_weight_growth-rate_plot
+#| echo: FALSE
+
+## Ok so now we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1. Let's visualize everything in a ggplot.
+
+ggplot(dGrowRate, aes(x = Diet, y = meanGrowRate, fill = Diet)) + geom_bar(stat = "identity") + labs(x = "Diet", y = "Mean Growth Rate", title = "Figure 2: Mean Growth Rate Bar Plot (rate per day)") + theme_minimal()
+
+```
+As shown in Figure 2 we see that diet 3 has chickens with the highest mean growth rates (per day). Diet 4 comes in second, then diet 2, then diet 1.
+```{r}
+#| label: chicken_weight_regression
+#| echo: FALSE 
+#| include: false
+
+## So if we are to infer that diet is a good predictor of growth rates (obviously in addition to time), we should see diet as a significant predictor of weight in a linear regression.
+Let's try that now.
+
+lmWeight = lm(Weight ~ Time + Diet, data = chicken_weight)
+summary(lmWeight)
+
+## So we see that both time and diet are significant predictors of weight.
+Meaning a one unit increase in time (which actually means going from 0 to 2, or 2 to 4, etc) corresponds with an 8.77 gram increase in weight.
+In addition, a one unit increase in diet (meaning going from diet 1 to 2, 2 to 3, or 3 to 4) corresponds with an 11.78 gram increase in weight.
+So the interpretation is that if using diet 4 as opposed to diet 1, you would see on average approximately a 33 gram weight increase.
+
+```
+
+```{r}
+#| label: chicken_weight_regression-plot
+#| echo: FALSE
+#| fig-cap: Regression of Weight on Time by Diet
+
+## Finally, plotting the regression.
+ggplot(chicken_weight, aes(x = Time, y = Weight, color = Diet, group = Diet)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE) + 
+  labs(x = "Time (days since birth)", y = "Weight (grams)", color = "Diet")
+
+```
+We found that both time and diet are significant predictors of weight.
+Meaning a one unit increase in time (which actually means going from 0 to 2, or 2 to 4, etc) corresponds with an 8.77 gram increase in weight.
+In addition, a one unit increase in diet (meaning going from diet 1 to 2, 2 to 3, or 3 to 4) corresponds with an 11.78 gram increase in weight.
+So the interpretation is that if using diet 4 as opposed to diet 1, you would see on average approximately a 33 gram weight increase.
+
+## Eggs 
+As shown in Table 1, we found that a component of our hypothesis was true: Big-Ass Chickens lay a Big-Ass-load of eggs.
 ```{r}
@@
 #| echo: FALSE 
-#| include: FALSE
+#| include: false
 
@@
 #| echo: FALSE
-#| include: FALSE
 
@@
 
+As shown in Table 2 and contrary to our hypothesis, however, there is a negative correlation between chicken weight and egg production within the Big-Ass Chicken demographic.
+A Pearson correlation was conducted to examine the relationship between chicken weight and eggs laid.
+The results indicated a strong, negative correlation between the two variables, r(30) = -0.93, p = .02.
+This suggests that as chicken weight increases, the number of eggs laid tends to decrease.
 ```{r}
@@
 
+However, as you can see in Figure 4, larger BAC's produced larger eggs, so really our main hypothesis of more chicken = more egg is like actually totally right when you think about it.
+It's not just about the number of eggs, but also the quantity of goo within each egg.
+Put another way, it's not just the size that matters, but how you use it....
+it being the egg goo.
 ```{r}
@@
 #| echo: FALSE
-
+#| fig-cap: Average Egg Weight by Chicken Breed and Egg Size
 # Create a new column for average egg weight based on breed and egg size
@@
   scale_fill_manual(values = c("Small" = "red", "Medium" = "yellow", "Large" = "green", "X-Large" = "blue")) +  # Custom colors
-  labs(title = "Average Egg Weight by Chicken Breed and Egg Size", 
-       x = "Chicken Breed", 
+  labs(x = "Chicken Breed", 
        y = "Average Egg Weight (grams)", 
@@
 ### 2. Self-Sufficiency and Food Security
-
 #### 2.1 Control Over Food Supply
@@
 ### 3. Social and Community Dimensions
-
 #### 3.1 Neighborhood Connections
@@
 ### 4. Practical Challenges and Adaptations
-
 #### 4.1 Time Commitment Reality
@@
 ### 5. Psychological and Emotional Benefits
-
 #### 5.1 Stress Reduction
